---
title: "Measuring centralities of reproducible cultural goods trade network"
author: "Author"
date: "2025-05-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(igraph)
```

## Steps: 
1. Reading the edgelist for reproducible cultural goods trade
2. Making 24 subsets of the edgelist with 24 different year columns
3. Doing the followings for each subset:
   a. Making igraph object from each one of them
   b. Reading each attribute file while merging the 'iso_o' values as vertex names with the igraph object
   c. making sure the igraph object used the vertex attributes
   d. Setting the edge weight
   e. Sanity checking for 
    * The graph is directed
    * Edge weights are valid-
    * Vertex names are unique and character
    * No self-loops or duplicate vertices
    * You’ve added only vertex attributes
4. Counting the number of nodes of all 24 networks to see if all matches
5. converting all 24 networks to 'wdnet' object
6. Finding out global and average local clustering coefficients
7. Finding out assortativity coefficient of four types
8. Making data frame with rows as times and the measures computed in step 6 and 7, saving that in the 'cleaned' sub-folder of the 'data' folder
9. Measuring  centralities of each network and making a data frame for the respective years network metrics and saving that as a csv file in the 'cleaned' sub-folder of th 'data' folder
10. Making a time series data for the global metrics of the network and saving a csv file in the 'cleaned' sub-folder of th 'data' folder

```{r}
r <- read.csv("../data/cleaned/reproducible_edgelist.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
```


## 2000
```{r}
y0 <- "X2000"   
r_y0 <- r[, c("iso_o", "iso_d", y0)]
r_y0 <- subset(r_y0, r_y0[[y0]] > 0)
att2000 <- read.csv("../data/cleaned/attribute2000.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re00 <- graph_from_data_frame(d = r_y0, directed = TRUE)
E(re00)$weight <- r_y0[[y0]]
is_directed(re00) 
length(E(re00)) == length(E(re00)$weight)
length(unique(V(re00)$name)) == gorder(re00) 
is.character(V(re00)$name) 
any(is.na(E(re00)$weight))      
any(!is.finite(E(re00)$weight)) 
edge_list_r1 <- as_data_frame(re00, what = "edges")
duplicated_rows_r1 <- duplicated(edge_list_r1[, c("from", "to")])
any(duplicated_rows_r1)  
length(unique(V(re00)$name))
```

```{r}
attify <- function(n_net, attr_df){
  V(n_net)$iso_o <- V(n_net)$name
  idx <- match(V(n_net)$name, attr_df$iso_o)
  V(n_net)$country <- attr_df$Country[idx]
  V(n_net)$D_log_gdp <- attr_df$D_log_gdp[idx]
  V(n_net)$D_log_gdp_pct <- attr_df$D_log_gdp_pct[idx]
  V(n_net)$log_population <- attr_df$log_population[idx]
  V(n_net)$log_trade_gdp_ratio <- attr_df$log_trade_gdp_ratio[idx]
  V(n_net)$landlocked <- attr_df$landlocked[idx]
  V(n_net)$continent <- attr_df$continent[idx]
  V(n_net)$lat <- attr_df$lat[idx]
  V(n_net)$lon <- attr_df$lon[idx]
  V(n_net)$development <- attr_df$development[idx]
  
  return(n_net)
}
re00 <- attify(re00, att2000)
vertex_attr_names(re00)
```

```{r}
library(wdnet)
class(re00)
h1 <- igraph_to_wdnet(re00)
class(h1)
summary(h1)
print(h1, node.attrs = TRUE, edge.attrs = TRUE)
```


```{r}
node_names1 <- h1$node.attr$iso_o 
pageRank_r0 <- centrality(h1, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r0 <- centrality(h1, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r0 <- centrality(h1, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r0 <- centrality(h1, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r01 <- clustcoef(h1, method = "Clemente")$total$localcc
lct_r02 <- clustcoef(h1, method = "Clemente")$out$localcc

centrality_rf0 <- data.frame(iso_o = node_names1, pageRank_repro = pageRank_r0, close_repro = closeness_r0, outdegree_repro = outdegree_r0, indegree_repro = indegree_r0, local_clust_tt_repro = lct_r01, local_clust_out_repro = lct_r02)
head(centrality_rf0)

write.csv(centrality_rf0, "../data/cleaned/network_metrics_reproducible2000.csv")
```

# 2001
```{r}
y1 <- "X2001"   
r_y1 <- r[, c("iso_o", "iso_d", y1)]
r_y1 <- subset(r_y1, r_y1[[y1]] > 0)
att2001 <- read.csv("../data/cleaned/attribute2001.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re01 <- graph_from_data_frame(d = r_y1, directed = TRUE)
E(re01)$weight <- r_y1[[y1]]
is_directed(re01) 
length(E(re01)) == length(E(re01)$weight)
length(unique(V(re01)$name)) == gorder(re01)  
is.character(V(re01)$name) 
any(is.na(E(re01)$weight))     
any(!is.finite(E(re01)$weight))
edge_list_r2 <- as_data_frame(re01, what = "edges")
duplicated_rows_r2 <- duplicated(edge_list_r2[, c("from", "to")])
any(duplicated_rows_r1)  
length(unique(V(re01)$name))
re01 <- attify(re01, att2001)
vertex_attr_names(re01)
```

```{r}
class(re01)
h2 <- igraph_to_wdnet(re01)
class(h2)
summary(h2)
print(h2, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names2 <- h2$node.attr$iso_o 
pageRank_r1 <- centrality(h2, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r1 <- centrality(h2, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r1 <- centrality(h2, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r1 <- centrality(h2, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r11 <- clustcoef(h2, method = "Clemente")$total$localcc
lct_r12 <- clustcoef(h2, method = "Clemente")$out$localcc

centrality_rf1 <- data.frame(iso_o = node_names2, pageRank_repro = pageRank_r1, close_repro = closeness_r1, outdegree_repro = outdegree_r1, indegree_repro = indegree_r1, local_clust_tt_repro = lct_r11, local_clust_out_repro = lct_r12)
head(centrality_rf1)

write.csv(centrality_rf1, "../data/cleaned/network_metrics_reproducible2001.csv")
```


## 2002
```{r}
y2 <- "X2002"   
r_y2 <- r[, c("iso_o", "iso_d", y2)]
r_y2 <- subset(r_y2, r_y2[[y2]] > 0)
att2002 <- read.csv("../data/cleaned/attribute2002.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re02 <- graph_from_data_frame(d = r_y2, directed = TRUE)
E(re02)$weight <- r_y2[[y2]]
is_directed(re02) 
length(E(re02)) == length(E(re02)$weight)
length(unique(V(re02)$name)) == gorder(re02)  
is.character(V(re02)$name) 
any(is.na(E(re02)$weight))     
any(!is.finite(E(re02)$weight)) 
edge_list_r3 <- as_data_frame(re02, what = "edges")
duplicated_rows_r3 <- duplicated(edge_list_r3[, c("from", "to")])
any(duplicated_rows_r3)  
length(unique(V(re02)$name))
re02 <- attify(re02, att2002)
vertex_attr_names(re02)
```

```{r}
class(re02)
h3 <- igraph_to_wdnet(re02)
class(h3)
summary(h3)
print(h3, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names3 <- h3$node.attr$iso_o 
pageRank_r2 <- centrality(h3, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r2 <- centrality(h3, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r2 <- centrality(h3, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r2 <- centrality(h3, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r21 <- clustcoef(h3, method = "Clemente")$total$localcc
lct_r22 <- clustcoef(h3, method = "Clemente")$out$localcc

centrality_rf2 <- data.frame(iso_o = node_names3, pageRank_repro = pageRank_r2, close_repro = closeness_r2, outdegree_repro = outdegree_r2, indegree_repro = indegree_r2,local_clust_tt_repro = lct_r21, local_clust_out_repro = lct_r22)
head(centrality_rf2)

write.csv(centrality_rf2, "../data/cleaned/network_metrics_reproducible2002.csv")
```


## 2003
```{r}
y3 <- "X2003"   
r_y3 <- r[, c("iso_o", "iso_d", y3)]
r_y3 <- subset(r_y3, r_y3[[y3]] > 0)
att2003 <- read.csv("../data/cleaned/attribute2003.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re03 <- graph_from_data_frame(d = r_y3, directed = TRUE)
E(re03)$weight <- r_y3[[y3]]
is_directed(re03) 
length(E(re03)) == length(E(re03)$weight)
length(unique(V(re03)$name)) == gorder(re03)  
is.character(V(re03)$name) 
any(is.na(E(re03)$weight))     
any(!is.finite(E(re03)$weight)) 
edge_list_r3 <- as_data_frame(re03, what = "edges")
duplicated_rows_r3 <- duplicated(edge_list_r3[, c("from", "to")])
any(duplicated_rows_r3)  
length(unique(V(re03)$name))
re03 <- attify(re03, att2003)
vertex_attr_names(re03)
```
```{r}
class(re03)
h4 <- igraph_to_wdnet(re03)
class(h4)
summary(h4)
print(h4, node.attrs = TRUE, edge.attrs = TRUE)
```
```{r}
node_names4 <- h4$node.attr$iso_o 
pageRank_r3 <- centrality(h4, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r3 <- centrality(h4, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r3 <- centrality(h4, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r3 <- centrality(h4, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r31 <- clustcoef(h4, method = "Clemente")$total$localcc
lct_r32 <- clustcoef(h4, method = "Clemente")$out$localcc

centrality_rf3 <- data.frame(iso_o = node_names4, pageRank_repro = pageRank_r3, close_repro = closeness_r3, outdegree_repro = outdegree_r3, indegree_repro = indegree_r3, local_clust_tt_repro = lct_r31, local_clust_out_repro = lct_r32)
head(centrality_rf3)

write.csv(centrality_rf3, "../data/cleaned/network_metrics_reproducible2003.csv")
```

# 2004
```{r}
y4 <- "X2004"   
r_y4 <- r[, c("iso_o", "iso_d", y4)]
r_y4 <- subset(r_y4, r_y4[[y4]] > 0)
att2004 <- read.csv("../data/cleaned/attribute2004.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re04 <- graph_from_data_frame(d = r_y4, directed = TRUE)
E(re04)$weight <- r_y4[[y4]]
is_directed(re04) 
length(E(re04)) == length(E(re04)$weight)
length(unique(V(re04)$name)) == gorder(re04)  
is.character(V(re04)$name) 
any(is.na(E(re04)$weight))    
any(!is.finite(E(re04)$weight)) 
edge_list_r4 <- as_data_frame(re04, what = "edges")
duplicated_rows_r4 <- duplicated(edge_list_r4[, c("from", "to")])
any(duplicated_rows_r4)  
length(unique(V(re04)$name))
re04 <- attify(re04, att2004)
vertex_attr_names(re04)
```

```{r}
class(re04)
h5 <- igraph_to_wdnet(re04)
class(h5)
summary(h5)
print(h5, node.attrs = TRUE, edge.attrs = TRUE)
```
```{r}
node_names5 <- h5$node.attr$iso_o 
pageRank_r4 <- centrality(h5, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r4 <- centrality(h5, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r4 <- centrality(h5, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r4 <- centrality(h5, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r41 <- clustcoef(h5, method = "Clemente")$total$localcc
lct_r42 <- clustcoef(h5, method = "Clemente")$out$localcc

centrality_rf4 <- data.frame(iso_o = node_names5, pageRank_repro = pageRank_r4, close_repro = closeness_r4, outdegree_repro = outdegree_r4, indegree_repro = indegree_r4, local_clust_tt_repro = lct_r41, local_clust_out_repro = lct_r42)
head(centrality_rf4)

write.csv(centrality_rf4, "../data/cleaned/network_metrics_reproducible2004.csv")
```


# 2005
```{r}
y5 <- "X2005"   
r_y5 <- r[, c("iso_o", "iso_d", y5)]
r_y5 <- subset(r_y5, r_y5[[y5]] > 0)
att2005 <- read.csv("../data/cleaned/attribute2005.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re05 <- graph_from_data_frame(d = r_y5, directed = TRUE)
E(re05)$weight <- r_y5[[y5]]
is_directed(re05) 
length(E(re05)) == length(E(re05)$weight)
length(unique(V(re05)$name)) == gorder(re05)  
is.character(V(re05)$name) 
any(is.na(E(re05)$weight))     
any(!is.finite(E(re05)$weight)) 
edge_list_r5 <- as_data_frame(re05, what = "edges")
duplicated_rows_r5 <- duplicated(edge_list_r5[, c("from", "to")])
any(duplicated_rows_r5)  
length(unique(V(re05)$name))
re05 <- attify(re05, att2005)
vertex_attr_names(re05)
```

```{r}
class(re05)
h6 <- igraph_to_wdnet(re05)
class(h6)
summary(h6)
print(h6, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names6 <- h6$node.attr$iso_o 
pageRank_r5 <- centrality(h6, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r5 <- centrality(h6, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r5 <- centrality(h6, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r5 <- centrality(h6, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r51 <- clustcoef(h6, method = "Clemente")$total$localcc
lct_r52 <- clustcoef(h6, method = "Clemente")$out$localcc

centrality_rf5 <- data.frame(iso_o = node_names6, pageRank_repro = pageRank_r5, close_repro = closeness_r5, outdegree_repro = outdegree_r5, indegree_repro = indegree_r5,local_clust_tt_repro = lct_r51, local_clust_out_repro = lct_r52)
head(centrality_rf5)

write.csv(centrality_rf5, "../data/cleaned/network_metrics_reproducible2005.csv")
```

# 2006
```{r}
y6 <- "X2006"   
r_y6 <- r[, c("iso_o", "iso_d", y6)]
r_y6 <- subset(r_y6, r_y6[[y6]] > 0)
att2006 <- read.csv("../data/cleaned/attribute2006.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re06 <- graph_from_data_frame(d = r_y6, directed = TRUE)
E(re06)$weight <- r_y6[[y6]]
is_directed(re06) 
length(E(re06)) == length(E(re06)$weight)
length(unique(V(re06)$name)) == gorder(re06)  
is.character(V(re06)$name) 
any(is.na(E(re06)$weight))      
any(!is.finite(E(re06)$weight)) 
edge_list_r6 <- as_data_frame(re06, what = "edges")
duplicated_rows_r6 <- duplicated(edge_list_r6[, c("from", "to")])
any(duplicated_rows_r6) 
length(unique(V(re06)$name))
re06 <- attify(re06, att2006)
vertex_attr_names(re06)

```

```{r}
class(re06)
h7 <- igraph_to_wdnet(re06)
class(h7)
summary(h7)
print(h7, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names7 <- h7$node.attr$iso_o 
pageRank_r6 <- centrality(h7, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r6 <- centrality(h7, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r6 <- centrality(h7, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r6 <- centrality(h7, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r61 <- clustcoef(h7, method = "Clemente")$total$localcc
lct_r62 <- clustcoef(h7, method = "Clemente")$out$localcc

centrality_rf6 <- data.frame(iso_o = node_names7, pageRank_repro = pageRank_r6, close_repro = closeness_r6, outdegree_repro = outdegree_r6, indegree_repro = indegree_r6, local_clust_tt_repro = lct_r61, local_clust_out_repro = lct_r62)
head(centrality_rf6)

write.csv(centrality_rf6, "../data/cleaned/network_metrics_reproducible2006.csv")

```

## 2007
```{r}
y7 <- "X2007"   
r_y7 <- r[, c("iso_o", "iso_d", y7)]
# Filter out edges with zero trade
r_y7 <- subset(r_y7, r_y7[[y7]] > 0)
att2007 <- read.csv("../data/cleaned/attribute2007.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re07 <- graph_from_data_frame(d = r_y7, directed = TRUE)
E(re07)$weight <- r_y7[[y7]]
is_directed(re07) 
length(E(re07)) == length(E(re07)$weight)
length(unique(V(re07)$name)) == gorder(re07)  # should be TRUE
is.character(V(re07)$name) 
any(is.na(E(re07)$weight))      # should be FALSE
any(!is.finite(E(re07)$weight)) # should be FALSE
edge_list_r7 <- as_data_frame(re07, what = "edges")
duplicated_rows_r7 <- duplicated(edge_list_r7[, c("from", "to")])
any(duplicated_rows_r7)  # should be FALSE
length(unique(V(re07)$name))
re07 <- attify(re07, att2007)
vertex_attr_names(re07)
```

```{r}
class(re07)
h8 <- igraph_to_wdnet(re07)
class(h8)
summary(h8)
print(h8, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names8 <- h8$node.attr$iso_o 
pageRank_r7 <- centrality(h8, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r7 <- centrality(h8, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))

outdegree_r7 <- centrality(h8, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r7 <- centrality(h8, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r71 <- clustcoef(h8, method = "Clemente")$total$localcc
lct_r72 <- clustcoef(h8, method = "Clemente")$out$localcc

centrality_rf7 <- data.frame(iso_o = node_names8, pageRank_repro = pageRank_r7, close_repro = closeness_r7, outdegree_repro = outdegree_r7, indegree_repro = indegree_r7, local_clust_tt_repro = lct_r71, local_clust_out_repro = lct_r72)
head(centrality_rf7)

write.csv(centrality_rf7, "../data/cleaned/network_metrics_reproducible2007.csv")
```


## 2008
```{r}
y8 <- "X2008"   
r_y8 <- r[, c("iso_o", "iso_d", y8)]
r_y8 <- subset(r_y8, r_y8[[y8]] > 0)
att2008 <- read.csv("../data/cleaned/attribute2008.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re08 <- graph_from_data_frame(d = r_y8, directed = TRUE)
E(re08)$weight <- r_y8[[y8]]
is_directed(re08) 
length(E(re08)) == length(E(re08)$weight)
length(unique(V(re08)$name)) == gorder(re08)  
is.character(V(re08)$name) 
any(is.na(E(re08)$weight))     
any(!is.finite(E(re08)$weight)) 
edge_list_r8 <- as_data_frame(re08, what = "edges")
duplicated_rows_r8 <- duplicated(edge_list_r8[, c("from", "to")])
any(duplicated_rows_r8)  
length(unique(V(re08)$name))
re08 <- attify(re08, att2008)
vertex_attr_names(re08)
```

```{r}
class(re08)
h9 <- igraph_to_wdnet(re08)
class(h9)
summary(h9)
print(h9, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names9 <- h9$node.attr$iso_o 
pageRank_r8 <- centrality(h9, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r8 <- centrality(h9, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r8 <- centrality(h9, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r8 <- centrality(h9, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r81 <- clustcoef(h9, method = "Clemente")$total$localcc
lct_r82 <- clustcoef(h9, method = "Clemente")$out$localcc

centrality_rf8 <- data.frame(iso_o = node_names9, pageRank_repro = pageRank_r8, close_repro = closeness_r8, outdegree_repro = outdegree_r8, indegree_repro = indegree_r8, local_clust_tt_repro = lct_r81, local_clust_out_repro = lct_r82)
head(centrality_rf8)

write.csv(centrality_rf8, "../data/cleaned/network_metrics_reproducible2008.csv")
```


## 2009
```{r}
y9 <- "X2009"   
r_y9 <- r[, c("iso_o", "iso_d", y9)]
r_y9 <- subset(r_y9, r_y9[[y9]] > 0)
att2009 <- read.csv("../data/cleaned/attribute2009.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re09 <- graph_from_data_frame(d = r_y9, directed = TRUE)
E(re09)$weight <- r_y9[[y9]]
is_directed(re09) 
length(E(re09)) == length(E(re09)$weight)
length(unique(V(re09)$name)) == gorder(re09)  
is.character(V(re09)$name) 
any(is.na(E(re09)$weight))      
any(!is.finite(E(re09)$weight))
edge_list_r9 <- as_data_frame(re09, what = "edges")
duplicated_rows_r9 <- duplicated(edge_list_r9[, c("from", "to")])
any(duplicated_rows_r9)  # should be FALSE
length(unique(V(re09)$name))
re09 <- attify(re09, att2009)
vertex_attr_names(re09)
```

```{r}
class(re09)
h10 <- igraph_to_wdnet(re09)
class(h10)
summary(h10)
print(h10, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names10 <- h10$node.attr$iso_o 
pageRank_r9 <- centrality(h10, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r9 <- centrality(h10, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r9 <- centrality(h10, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r9 <- centrality(h10, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r91 <- clustcoef(h10, method = "Clemente")$total$localcc
lct_r92 <- clustcoef(h10, method = "Clemente")$out$localcc

centrality_rf9 <- data.frame(iso_o = node_names10, pageRank_repro = pageRank_r9, close_repro = closeness_r9, outdegree_repro = outdegree_r9, indegree_repro = indegree_r9, local_clust_tt_repro = lct_r91, local_clust_out_repro = lct_r92)
head(centrality_rf9)

write.csv(centrality_rf9, "../data/cleaned/network_metrics_reproducible2009.csv")
```


## 2010
```{r}
y10 <- "X2010"   
r_y10 <- r[, c("iso_o", "iso_d", y10)]
r_y10 <- subset(r_y10, r_y10[[y10]] > 0)
att2010 <- read.csv("../data/cleaned/attribute2010.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re10 <- graph_from_data_frame(d = r_y10, directed = TRUE)
E(re10)$weight <- r_y10[[y10]]
is_directed(re10) 
length(E(re10)) == length(E(re10)$weight)
length(unique(V(re10)$name)) == gorder(re10) 
is.character(V(re10)$name) 
any(is.na(E(re10)$weight))      
any(!is.finite(E(re10)$weight)) 
edge_list_r10 <- as_data_frame(re10, what = "edges")
duplicated_rows_r10 <- duplicated(edge_list_r10[, c("from", "to")])
any(duplicated_rows_r10)  
length(unique(V(re10)$name))
re10 <- attify(re10, att2010)
vertex_attr_names(re10)
```

```{r}
class(re10)
h11 <- igraph_to_wdnet(re10)
class(h11)
summary(h11)
print(h11, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names11 <- h11$node.attr$iso_o 
pageRank_r10 <- centrality(h11, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r10 <- centrality(h11, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r10 <- centrality(h11, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r10 <- centrality(h11, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r101 <- clustcoef(h11, method = "Clemente")$total$localcc
lct_r102 <- clustcoef(h11, method = "Clemente")$out$localcc

centrality_rf10 <- data.frame(iso_o = node_names11, pageRank_repro = pageRank_r10, close_repro = closeness_r10, outdegree_repro = outdegree_r10, indegree_repro = indegree_r10, local_clust_tt_repro = lct_r101, local_clust_out_repro = lct_r102)
head(centrality_rf10)

write.csv(centrality_rf10, "../data/cleaned/network_metrics_reproducible2010.csv")
```

## 2011
```{r}
y11 <- "X2011"   
r_y11 <- r[, c("iso_o", "iso_d", y11)]
r_y11 <- subset(r_y11, r_y11[[y11]] > 0)
att2011 <- read.csv("../data/cleaned/attribute2011.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re11 <- graph_from_data_frame(d = r_y11, directed = TRUE)
E(re11)$weight <- r_y11[[y11]]
is_directed(re11) 
length(E(re11)) == length(E(re11)$weight)
length(unique(V(re11)$name)) == gorder(re11)  
is.character(V(re11)$name) 
any(is.na(E(re11)$weight))      
any(!is.finite(E(re11)$weight)) 
edge_list_r11 <- as_data_frame(re11, what = "edges")
duplicated_rows_r11 <- duplicated(edge_list_r11[, c("from", "to")])
any(duplicated_rows_r11)  
length(unique(V(re11)$name))
re11 <- attify(re11, att2011)
vertex_attr_names(re11)
```

```{r}
class(re11)
h12 <- igraph_to_wdnet(re11)
class(h12)
summary(h12)
print(h12, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names12 <- h12$node.attr$iso_o 
pageRank_r11 <- centrality(h12, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r11 <- centrality(h12, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r11 <- centrality(h12, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r11 <- centrality(h12, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r111 <- clustcoef(h12, method = "Clemente")$total$localcc
lct_r112 <- clustcoef(h12, method = "Clemente")$out$localcc

centrality_rf11 <- data.frame(iso_o = node_names12, pageRank_repro = pageRank_r11, close_repro = closeness_r11, outdegree_repro = outdegree_r11, indegree_repro = indegree_r11,local_clust_tt_repro = lct_r111, local_clust_out_repro = lct_r112)
head(centrality_rf11)

write.csv(centrality_rf11, "../data/cleaned/network_metrics_reproducible2011.csv")
```


## 2012
```{r}
y12 <- "X2012"   
r_y12 <- r[, c("iso_o", "iso_d", y12)]
r_y12 <- subset(r_y12, r_y12[[y12]] > 0)
att2012 <- read.csv("../data/cleaned/attribute2012.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re12 <- graph_from_data_frame(d = r_y12, directed = TRUE)
E(re12)$weight <- r_y12[[y12]]
is_directed(re12) 
length(E(re12)) == length(E(re12)$weight)
length(unique(V(re12)$name)) == gorder(re12)  
is.character(V(re12)$name) 
any(is.na(E(re12)$weight))      
any(!is.finite(E(re12)$weight)) 
edge_list_r12 <- as_data_frame(re12, what = "edges")
duplicated_rows_r12 <- duplicated(edge_list_r12[, c("from", "to")])
any(duplicated_rows_r12)  
length(unique(V(re12)$name))
re12 <- attify(re12, att2012)
vertex_attr_names(re12)
```

```{r}
class(re12)
h13 <- igraph_to_wdnet(re12)
class(h13)
summary(h13)
print(h13, node.attrs = TRUE, edge.attrs = TRUE)

```

```{r}
node_names13 <- h13$node.attr$iso_o 
pageRank_r12 <- centrality(h13, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r12 <- centrality(h13, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r12 <- centrality(h13, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r12 <- centrality(h13, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r121 <- clustcoef(h13, method = "Clemente")$total$localcc
lct_r122 <- clustcoef(h13, method = "Clemente")$out$localcc

centrality_rf12 <- data.frame(iso_o = node_names13, pageRank_repro = pageRank_r12, close_repro = closeness_r12, outdegree_repro = outdegree_r12, indegree_repro = indegree_r12, local_clust_tt_repro = lct_r121, local_clust_out_repro = lct_r122)
head(centrality_rf12)

write.csv(centrality_rf12, "../data/cleaned/network_metrics_reproducible2012.csv")
```

## 2013
```{r}
y13 <- "X2013"   
r_y13 <- r[, c("iso_o", "iso_d", y13)]
r_y13 <- subset(r_y13, r_y13[[y13]] > 0)
att2013 <- read.csv("../data/cleaned/attribute2013.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re13 <- graph_from_data_frame(d = r_y13, directed = TRUE)
E(re13)$weight <- r_y13[[y13]]
is_directed(re13) 
length(E(re13)) == length(E(re13)$weight)
length(unique(V(re13)$name)) == gorder(re13)  
is.character(V(re13)$name) 
any(is.na(E(re13)$weight))      
any(!is.finite(E(re13)$weight)) 
edge_list_r13 <- as_data_frame(re13, what = "edges")
duplicated_rows_r13 <- duplicated(edge_list_r13[, c("from", "to")])
any(duplicated_rows_r13)  
length(unique(V(re13)$name))
re13 <- attify(re13, att2013)
vertex_attr_names(re13)
```

```{r}
class(re13)
h14 <- igraph_to_wdnet(re13)
class(h14)
summary(h14)
print(h14, node.attrs = TRUE, edge.attrs = TRUE)

```

```{r}
node_names14 <- h14$node.attr$iso_o 
pageRank_r13 <- centrality(h14, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r13 <- centrality(h14, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r13 <- centrality(h14, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r13 <- centrality(h14, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r131 <- clustcoef(h14, method = "Clemente")$total$localcc
lct_r132 <- clustcoef(h14, method = "Clemente")$out$localcc

centrality_rf13 <- data.frame(iso_o = node_names14, pageRank_repro = pageRank_r13, close_repro = closeness_r13, outdegree_repro = outdegree_r13, indegree_repro = indegree_r13,local_clust_tt_repro = lct_r131, local_clust_out_repro = lct_r132)
head(centrality_rf13)

write.csv(centrality_rf13, "../data/cleaned/network_metrics_reproducible2013.csv")
```


## 2014
```{r}
y14 <- "X2014"   
r_y14 <- r[, c("iso_o", "iso_d", y14)]
r_y14 <- subset(r_y14, r_y14[[y14]] > 0)
att2014 <- read.csv("../data/cleaned/attribute2014.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re14 <- graph_from_data_frame(d = r_y14, directed = TRUE)
E(re14)$weight <- r_y14[[y14]]
is_directed(re14) 
length(E(re14)) == length(E(re14)$weight)
length(unique(V(re14)$name)) == gorder(re14)  
is.character(V(re14)$name) 
any(is.na(E(re14)$weight))     
any(!is.finite(E(re14)$weight)) 
edge_list_r14 <- as_data_frame(re14, what = "edges")
duplicated_rows_r14 <- duplicated(edge_list_r14[, c("from", "to")])
any(duplicated_rows_r14) 
length(unique(V(re14)$name))
re14 <- attify(re14, att2014)
vertex_attr_names(re14)
```

```{r}
class(re14)
h15 <- igraph_to_wdnet(re14)
class(h15)
summary(h15)
print(h15, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names15 <- h15$node.attr$iso_o 
pageRank_r14 <- centrality(h15, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r14 <- centrality(h15, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r14 <- centrality(h15, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r14 <- centrality(h15, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r141 <- clustcoef(h15, method = "Clemente")$total$localcc
lct_r142 <- clustcoef(h15, method = "Clemente")$out$localcc

centrality_rf14 <- data.frame(iso_o = node_names15, pageRank_repro = pageRank_r14, close_repro = closeness_r14, outdegree_repro = outdegree_r14, indegree_repro = indegree_r14, local_clust_tt_repro = lct_r141, local_clust_out_repro = lct_r142)
head(centrality_rf14)

write.csv(centrality_rf14, "../data/cleaned/network_metrics_reproducible2014.csv")
```

## 2015
```{r}
y15 <- "X2015"   
r_y15 <- r[, c("iso_o", "iso_d", y15)]
r_y15 <- subset(r_y15, r_y15[[y15]] > 0)
att2015 <- read.csv("../data/cleaned/attribute2015.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re15 <- graph_from_data_frame(d = r_y15, directed = TRUE)
E(re15)$weight <- r_y15[[y15]]
is_directed(re15) 
length(E(re15)) == length(E(re15)$weight)
length(unique(V(re15)$name)) == gorder(re15)  
is.character(V(re15)$name) 
any(is.na(E(re15)$weight))      
any(!is.finite(E(re15)$weight)) 
edge_list_r15 <- as_data_frame(re15, what = "edges")
duplicated_rows_r15 <- duplicated(edge_list_r15[, c("from", "to")])
any(duplicated_rows_r15)  
length(unique(V(re15)$name))
re15 <- attify(re15, att2015)
vertex_attr_names(re15)
```

```{r}
class(re15)
h16 <- igraph_to_wdnet(re15)
class(h16)
summary(h16)
print(h16, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names16 <- h16$node.attr$iso_o 
pageRank_r15 <- centrality(h16, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r15 <- centrality(h16, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r15 <- centrality(h16, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r15 <- centrality(h16, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r151 <- clustcoef(h16, method = "Clemente")$total$localcc
lct_r152 <- clustcoef(h16, method = "Clemente")$out$localcc

centrality_rf15 <- data.frame(iso_o = node_names16, pageRank_repro = pageRank_r15, close_repro = closeness_r15, outdegree_repro = outdegree_r15, indegree_repro = indegree_r15, local_clust_tt_repro = lct_r151, local_clust_out_repro = lct_r152)
head(centrality_rf15)

write.csv(centrality_rf15, "../data/cleaned/network_metrics_reproducible2015.csv")
```


# 2016
```{r}
y16 <- "X2016"   
r_y16 <- r[, c("iso_o", "iso_d", y16)]
r_y16 <- subset(r_y16, r_y16[[y16]] > 0)
att2016 <- read.csv("../data/cleaned/attribute2016.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re16 <- graph_from_data_frame(d = r_y16, directed = TRUE)
E(re16)$weight <- r_y16[[y16]]
is_directed(re16) 
length(E(re16)) == length(E(re16)$weight)
length(unique(V(re16)$name)) == gorder(re16)  
is.character(V(re16)$name) 
any(is.na(E(re16)$weight))      
any(!is.finite(E(re16)$weight)) 
edge_list_r16 <- as_data_frame(re16, what = "edges")
duplicated_rows_r16 <- duplicated(edge_list_r16[, c("from", "to")])
any(duplicated_rows_r16)  
length(unique(V(re16)$name))
re16 <- attify(re16, att2016)
vertex_attr_names(re16)
```

```{r}
class(re16)
h17 <- igraph_to_wdnet(re16)
class(h17)
summary(h17)
print(h17, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names17 <- h17$node.attr$iso_o 
pageRank_r16 <- centrality(h17, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r16 <- centrality(h17, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r16 <- centrality(h17, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r16 <- centrality(h17, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r161 <- clustcoef(h17, method = "Clemente")$total$localcc
lct_r162 <- clustcoef(h17, method = "Clemente")$out$localcc

centrality_rf16 <- data.frame(iso_o = node_names17, pageRank_repro = pageRank_r16, close_repro = closeness_r16, outdegree_repro = outdegree_r16, indegree_repro = indegree_r16,local_clust_tt_repro = lct_r161, local_clust_out_repro = lct_r162)
head(centrality_rf16)

write.csv(centrality_rf16, "../data/cleaned/network_metrics_reproducible2016.csv")
```

## 2017
```{r}
y17 <- "X2017"   
r_y17 <- r[, c("iso_o", "iso_d", y17)]
r_y17 <- subset(r_y17, r_y17[[y17]] > 0)
att2017 <- read.csv("../data/cleaned/attribute2017.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re17 <- graph_from_data_frame(d = r_y17, directed = TRUE)
E(re17)$weight <- r_y17[[y17]]
is_directed(re17) 
length(E(re17)) == length(E(re17)$weight)
length(unique(V(re17)$name)) == gorder(re17)  
is.character(V(re17)$name) 
any(is.na(E(re17)$weight))      
any(!is.finite(E(re17)$weight)) 
edge_list_r17 <- as_data_frame(re17, what = "edges")
duplicated_rows_r17 <- duplicated(edge_list_r17[, c("from", "to")])
any(duplicated_rows_r17)  
length(unique(V(re17)$name))
re17 <- attify(re17, att2017)
vertex_attr_names(re17)
```

```{r}
class(re17)
h18 <- igraph_to_wdnet(re17)
class(h18)
summary(h18)
print(h18, node.attrs = TRUE, edge.attrs = TRUE)

```

```{r}
node_names18 <- h18$node.attr$iso_o 
pageRank_r17 <- centrality(h18, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r17 <- centrality(h18, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r17 <- centrality(h18, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r17 <- centrality(h18, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r171 <- clustcoef(h18, method = "Clemente")$total$localcc
lct_r172 <- clustcoef(h18, method = "Clemente")$out$localcc

centrality_rf17 <- data.frame(iso_o = node_names18, pageRank_repro = pageRank_r17, close_repro = closeness_r17, outdegree_repro = outdegree_r17, indegree_repro = indegree_r17, local_clust_tt_repro = lct_r171, local_clust_out_repro = lct_r172)
head(centrality_rf17)

write.csv(centrality_rf17, "../data/cleaned/network_metrics_reproducible2017.csv")
```

## 2018
```{r}
y18 <- "X2018"   
r_y18 <- r[, c("iso_o", "iso_d", y18)]
r_y18 <- subset(r_y18, r_y18[[y18]] > 0)
att2018 <- read.csv("../data/cleaned/attribute2018.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re18 <- graph_from_data_frame(d = r_y18, directed = TRUE)
E(re18)$weight <- r_y18[[y18]]
is_directed(re18) 
length(E(re18)) == length(E(re18)$weight)
length(unique(V(re18)$name)) == gorder(re18)  
is.character(V(re18)$name) 
any(is.na(E(re18)$weight))      
any(!is.finite(E(re18)$weight)) 
edge_list_r18 <- as_data_frame(re18, what = "edges")
duplicated_rows_r18 <- duplicated(edge_list_r18[, c("from", "to")])
any(duplicated_rows_r18)  
length(unique(V(re18)$name))
re18 <- attify(re18, att2018)
vertex_attr_names(re18)
```

```{r}
class(re18)
h19<- igraph_to_wdnet(re18)
class(h19)
summary(h19)
vertex_attr_names(re18)
print(h19, node.attrs= TRUE, edge.attrs= TRUE)
```

```{r}
node_names19 <- h19$node.attr$iso_o 
pageRank_r18 <- centrality(h19, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r18 <- centrality(h19, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r18 <- centrality(h19, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r18 <- centrality(h19, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r181 <- clustcoef(h19, method = "Clemente")$total$localcc
lct_r182 <- clustcoef(h19, method = "Clemente")$out$localcc

centrality_rf18 <- data.frame(iso_o = node_names19, pageRank_repro = pageRank_r18, close_repro = closeness_r18, outdegree_repro = outdegree_r18, indegree_repro = indegree_r18, local_clust_tt_repro = lct_r181, local_clust_out_repro = lct_r182)
head(centrality_rf18)

write.csv(centrality_rf18, "../data/cleaned/network_metrics_reproducible2018.csv")
```

## 2019
```{r}
y19 <- "X2019"   
r_y19 <- r[, c("iso_o", "iso_d", y19)]
r_y19 <- subset(r_y19, r_y19[[y19]] > 0)
att2019 <- read.csv("../data/cleaned/attribute2019.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re19 <- graph_from_data_frame(d = r_y19, directed = TRUE)
E(re19)$weight <- r_y19[[y19]]
is_directed(re19) 
length(E(re19)) == length(E(re19)$weight)
length(unique(V(re19)$name)) == gorder(re19)  
is.character(V(re19)$name) 
any(is.na(E(re19)$weight))     
any(!is.finite(E(re19)$weight)) 
edge_list_r19 <- as_data_frame(re19, what = "edges")
duplicated_rows_r19 <- duplicated(edge_list_r19[, c("from", "to")])
any(duplicated_rows_r19)  
length(unique(V(re19)$name))
re19 <- attify(re19, att2019)
vertex_attr_names(re19)
```

```{r}
class(re19)
h20<- igraph_to_wdnet(re19)
class(h20)
summary(h20)
vertex_attr_names(re19)
print(h20, node.attrs= TRUE, edge.attrs= TRUE)
```

```{r}
node_names20 <- h20$node.attr$iso_o 
pageRank_r19 <- centrality(h20, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r19 <- centrality(h20, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r19 <- centrality(h20, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r19 <- centrality(h20, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r191 <- clustcoef(h20, method = "Clemente")$total$localcc
lct_r192 <- clustcoef(h20, method = "Clemente")$out$localcc

centrality_rf19 <- data.frame(iso_o = node_names20, pageRank_repro = pageRank_r19, close_repro = closeness_r19, outdegree_repro = outdegree_r19, indegree_repro = indegree_r19, local_clust_tt_repro = lct_r191, local_clust_out_repro = lct_r192)
head(centrality_rf19)

write.csv(centrality_rf19, "../data/cleaned/network_metrics_reproducible2019.csv")
```

# 2020
```{r}
y20 <- "X2020"   
r_y20 <- r[, c("iso_o", "iso_d", y20)]
r_y20 <- subset(r_y20, r_y20[[y20]] > 0)
att2020 <- read.csv("../data/cleaned/attribute2020.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re20 <- graph_from_data_frame(d = r_y20, directed = TRUE)
E(re20)$weight <- r_y20[[y20]]
is_directed(re20) 
length(E(re20)) == length(E(re20)$weight)
length(unique(V(re20)$name)) == gorder(re20)  
is.character(V(re20)$name) 
any(is.na(E(re20)$weight))      
any(!is.finite(E(re20)$weight))
edge_list_r19 <- as_data_frame(re20, what = "edges")
duplicated_rows_r19 <- duplicated(edge_list_r19[, c("from", "to")])
any(duplicated_rows_r19)  
length(unique(V(re20)$name))
re20 <- attify(re20, att2020)
vertex_attr_names(re20)
```

```{r}
class(re20)
h21<- igraph_to_wdnet(re20)
class(h21)
summary(h21)
vertex_attr_names(re20)
print(h21, node.attrs= TRUE, edge.attrs= TRUE)
```

```{r}
node_names21 <- h21$node.attr$iso_o 
pageRank_r20 <- centrality(h21, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r20 <- centrality(h21, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))

outdegree_r20 <- centrality(h21, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r20 <- centrality(h21, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r201 <- clustcoef(h21, method = "Clemente")$total$localcc
lct_r202 <- clustcoef(h21, method = "Clemente")$out$localcc

centrality_rf20 <- data.frame(iso_o = node_names21, pageRank_repro = pageRank_r20, close_repro = closeness_r20, outdegree_repro = outdegree_r20, indegree_repro = indegree_r20, local_clust_tt_repro = lct_r201, local_clust_out_repro = lct_r202)
head(centrality_rf20)

write.csv(centrality_rf20, "../data/cleaned/network_metrics_reproducible2020.csv")
```

# 2021
```{r}
y21 <- "X2021"   
r_y21 <- r[, c("iso_o", "iso_d", y21)]
r_y21 <- subset(r_y21, r_y21[[y21]] > 0)
att2021 <- read.csv("../data/cleaned/attribute2021.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re21 <- graph_from_data_frame(d = r_y21, directed = TRUE)
E(re21)$weight <- r_y21[[y21]]
is_directed(re21) 
length(E(re21)) == length(E(re21)$weight)
length(unique(V(re21)$name)) == gorder(re21) 
is.character(V(re21)$name) 
any(is.na(E(re21)$weight))      
any(!is.finite(E(re21)$weight)) 
edge_list_r21 <- as_data_frame(re21, what = "edges")
duplicated_rows_r21 <- duplicated(edge_list_r21[, c("from", "to")])
any(duplicated_rows_r21)  
length(unique(V(re21)$name))
re21 <- attify(re21, att2021)
vertex_attr_names(re21)
```

```{r}
class(re21)
h22 <- igraph_to_wdnet(re21)
class(h22)
summary(h22)
vertex_attr_names(re21)
print(h22, node.attrs= TRUE, edge.attrs= TRUE)
```

```{r}
node_names22 <- h22$node.attr$iso_o 
pageRank_r21 <- centrality(h22, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r21 <- centrality(h22, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r21 <- centrality(h22, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r21 <- centrality(h22, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r211 <- clustcoef(h22, method = "Clemente")$total$localcc
lct_r212 <- clustcoef(h22, method = "Clemente")$out$localcc

centrality_rf21 <- data.frame(iso_o = node_names22, pageRank_repro = pageRank_r21, close_repro = closeness_r21, outdegree_repro = outdegree_r21, indegree_repro = indegree_r21,local_clust_tt_repro = lct_r211, local_clust_out_repro = lct_r212)
head(centrality_rf21)

write.csv(centrality_rf21, "../data/cleaned/network_metrics_reproducible2021.csv")
```

# 2022
```{r}
y22 <- "X2022"   
r_y22 <- r[, c("iso_o", "iso_d", y22)]
r_y22 <- subset(r_y22, r_y22[[y22]] > 0)
att2022 <- read.csv("../data/cleaned/attribute2022.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re22 <- graph_from_data_frame(d = r_y22, directed = TRUE)
E(re22)$weight <- r_y22[[y22]]
is_directed(re22) 
length(E(re22)) == length(E(re22)$weight)
length(unique(V(re22)$name)) == gorder(re22) 
is.character(V(re22)$name) 
any(is.na(E(re22)$weight))      
any(!is.finite(E(re22)$weight)) 
edge_list_r22 <- as_data_frame(re22, what = "edges")
duplicated_rows_r22 <- duplicated(edge_list_r22[, c("from", "to")])
any(duplicated_rows_r22)  
length(unique(V(re22)$name))
re22 <- attify(re22, att2022)
vertex_attr_names(re22)
```

```{r}
class(re22)
h23 <- igraph_to_wdnet(re22)
class(h23)
summary(h23)
vertex_attr_names(re22)
print(h23, node.attrs= TRUE, edge.attrs= TRUE)
```

```{r}
node_names23 <- h23$node.attr$iso_o 
pageRank_r22 <- centrality(h23, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r22 <- centrality(h23, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))

outdegree_r22 <- centrality(h23, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r22 <- centrality(h23, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r221 <- clustcoef(h23, method = "Clemente")$total$localcc
lct_r222 <- clustcoef(h23, method = "Clemente")$out$localcc

centrality_rf22 <- data.frame(iso_o = node_names23, pageRank_repro = pageRank_r22, close_repro = closeness_r22, outdegree_repro = outdegree_r22, indegree_repro = indegree_r22, local_clust_tt_repro = lct_r221, local_clust_out_repro = lct_r222)
head(centrality_rf22)

write.csv(centrality_rf22, "../data/cleaned/network_metrics_reproducible2022.csv")
```

#2023
```{r}
y23 <- "X2023"   
r_y23 <- r[, c("iso_o", "iso_d", y23)]
r_y23 <- subset(r_y23, r_y23[[y23]] > 0)
att2023 <- read.csv("../data/cleaned/attribute2023.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
re23 <- graph_from_data_frame(d = r_y23, directed = TRUE)
E(re23)$weight <- r_y23[[y23]]
is_directed(re23) 
length(E(re23)) == length(E(re23)$weight)
length(unique(V(re23)$name)) == gorder(re23)  
is.character(V(re23)$name) 
any(is.na(E(re23)$weight))     
any(!is.finite(E(re23)$weight)) 
edge_list_r23 <- as_data_frame(re23, what = "edges")
duplicated_rows_r23 <- duplicated(edge_list_r23[, c("from", "to")])
any(duplicated_rows_r23)  
length(unique(V(re23)$name))
re23 <- attify(re23, att2023)
vertex_attr_names(re23)
```

```{r}
class(re23)
h24 <- igraph_to_wdnet(re23)
class(h24)
summary(h24)
vertex_attr_names(re23)
print(h24, node.attrs= TRUE, edge.attrs= TRUE)
```

```{r}
node_names24 <- h24$node.attr$iso_o 
pageRank_r23 <- centrality(h24, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_r23 <- centrality(h24, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_r23 <- centrality(h24, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_r23 <- centrality(h24, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_r231 <- clustcoef(h24, method = "Clemente")$total$localcc
lct_r232 <- clustcoef(h24, method = "Clemente")$out$localcc

centrality_rf23 <- data.frame(iso_o = node_names24, pageRank_repro = pageRank_r23, close_repro = closeness_r23, outdegree_repro = outdegree_r23, indegree_repro = indegree_r23,local_clust_tt_repro = lct_r231, local_clust_out_repro = lct_r232)
head(centrality_rf23)

write.csv(centrality_rf23, "../data/cleaned/network_metrics_reproducible2023.csv")
```


```{r}
metric_time_r <- data.frame(TIME_PERIOD = c(2000, 2001, 2002, 2003, 2004, 2005, 2006, 2007, 2008,
                                          2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017,
                                          2018, 2019, 2020, 2021, 2022, 2023),
                    Global_CC_Cl_repro = c(clustcoef(h1, method ="Clemente")$total$globalcc,
                                         clustcoef(h2, method = "Clemente")$total$globalcc,
                                         clustcoef(h3, method = "Clemente")$total$globalcc,
                                         clustcoef(h4, method = "Clemente")$total$globalcc,
                                         clustcoef(h5, method = "Clemente")$total$globalcc,
                                         clustcoef(h6, method = "Clemente")$total$globalcc,
                                         clustcoef(h7, method ="Clemente")$total$globalcc,
                                         clustcoef(h8, method = "Clemente")$total$globalcc,
                                         clustcoef(h9, method = "Clemente")$total$globalcc,
                                         clustcoef(h10, method = "Clemente")$total$globalcc,
                                         clustcoef(h11, method = "Clemente")$total$globalcc,
                                         clustcoef(h12, method = "Clemente")$total$globalcc,
                                         clustcoef(h13, method ="Clemente")$total$globalcc,
                                         clustcoef(h14, method = "Clemente")$total$globalcc,
                                         clustcoef(h15, method = "Clemente")$total$globalcc,
                                         clustcoef(h16, method = "Clemente")$total$globalcc,
                                         clustcoef(h17, method = "Clemente")$total$globalcc,
                                         clustcoef(h18, method = "Clemente")$total$globalcc,
                                         clustcoef(h19, method ="Clemente")$total$globalcc,
                                         clustcoef(h20, method = "Clemente")$total$globalcc,
                                         clustcoef(h21, method = "Clemente")$total$globalcc,
                                         clustcoef(h22, method = "Clemente")$total$globalcc,
                                         clustcoef(h23, method = "Clemente")$total$globalcc,
                                         clustcoef(h24, method = "Clemente")$total$globalcc),
                    Global_CC_Fg_repro = c(clustcoef(h1, method = "Clemente")$out$globalcc,
                                         clustcoef(h2, method = "Clemente")$out$globalcc,
                                         clustcoef(h3, method = "Clemente")$out$globalcc,
                                         clustcoef(h4, method = "Clemente")$out$globalcc,
                                         clustcoef(h5, method = "Clemente")$out$globalcc,
                                         clustcoef(h6, method = "Clemente")$out$globalcc,
                                         clustcoef(h7, method = "Clemente")$out$globalcc,
                                         clustcoef(h8, method = "Clemente")$out$globalcc,
                                         clustcoef(h9, method = "Clemente")$out$globalcc,
                                         clustcoef(h10, method = "Clemente")$out$globalcc,
                                         clustcoef(h11, method = "Clemente")$out$globalcc,
                                         clustcoef(h12, method = "Clemente")$out$globalcc,
                                         clustcoef(h13, method = "Clemente")$out$globalcc,
                                         clustcoef(h14, method = "Clemente")$out$globalcc,
                                         clustcoef(h15, method = "Clemente")$out$globalcc,
                                         clustcoef(h16, method = "Clemente")$out$globalcc,
                                         clustcoef(h17, method = "Clemente")$out$globalcc,
                                         clustcoef(h18, method = "Clemente")$out$globalcc,
                                         clustcoef(h19, method = "Clemente")$out$globalcc,
                                         clustcoef(h20, method = "Clemente")$out$globalcc,
                                         clustcoef(h21, method = "Clemente")$out$globalcc,
                                         clustcoef(h22, method = "Clemente")$out$globalcc,
                                         clustcoef(h23, method = "Clemente")$out$globalcc,
                                         clustcoef(h24, method = "Clemente")$out$globalcc),
                   Avg_CC_Cl_repro = c(mean(clustcoef(h1, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h2, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h3, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h4, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h5, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h6, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h7, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h8, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h9, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h10, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h11, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h12, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h13, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h14, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h15, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h16, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h17, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h18, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h19, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h20, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h21, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h22, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h23, method = "Clemente")$total$localcc),
                                      mean(clustcoef(h24, method = "Clemente")$total$localcc)),
                   Avg_CC_Fg_repro = c(mean(clustcoef(h1, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h2, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h3, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h4, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h5, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h6, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h7, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h8, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h9, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h10, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h11, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h12, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h13, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h14, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h15, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h16, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h17, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h18, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h19, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h20, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h21, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h21, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h23, method = "Clemente")$out$localcc),
                                      mean(clustcoef(h24, method = "Clemente")$out$localcc)),
                  assortcoef_repro = c(assortcoef(h1), 
                                      assortcoef(h2), 
                                      assortcoef(h3), 
                                      assortcoef(h4),
                                      assortcoef(h5), 
                                      assortcoef(h6), 
                                      assortcoef(h7), 
                                      assortcoef(h8),
                                      assortcoef(h9), 
                                      assortcoef(h10), 
                                      assortcoef(h11), 
                                      assortcoef(h12),
                                      assortcoef(h13), 
                                      assortcoef(h14), 
                                      assortcoef(h15), 
                                      assortcoef(h16),
                                      assortcoef(h17), 
                                      assortcoef(h18), 
                                      assortcoef(h19), 
                                      assortcoef(h20),
                                      assortcoef(h21), 
                                      assortcoef(h22), 
                                      assortcoef(h23), 
                                      assortcoef(h24)))

```

```{r}
metric_time_r
```


```{r}
write.csv(metric_time_r, "../data/cleaned/network_metrics_timeseries_reproducible.csv")
```


