---
title: "Measuring centralities of non-cultural goods trade networks"
author: "Author"
date: "2025-05-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(igraph)
```

## Steps: 
1. Reading the edgelist for total goods trade
2. Making 24 subsets of the edgelist with 24 different year columns
3. Doing the followings for each subset:
   a. Making igraph object from each one of them
   b. Reading each attribute file while merging the 'iso_o' values as vertex names with the igraph object
   c. making sure the igraph object used the vertex attributes
   d. Setting the edge weight
   e. Sanity checking for 
    * The graph is directed
    * Edge weights are valid-
    * Vertex names are unique and character
    * No self-loops or duplicate vertices
    * You’ve added only vertex attributes
4. Counting the number of nodes of all 24 networks to see if all matches
5. converting all 24 networks to 'wdnet' object
6. Finding out global and average local clustering coefficients
7. Finding out assortativity coefficient of four types
8. Making data frame with rows as times and the measures computed in step 6 and 7, saving that in the 'cleaned' sub-folder of the 'data' folder
9. Measuring  centralities of each network and making a data frame for the respective years network metrices and saving that as a csv file in the 'cleaned' sub-folder of th 'data' folder
10. Making a time series data for the global metrics of the network and saving a csv file in the 'cleaned' sub-folder of th 'data' folder

```{r}
t <- read.csv("../data/cleaned/total_edgelist.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
```


## 2000
```{r}
y0 <- "X2000"   
t_y0 <- t[, c("iso_o", "iso_d", y0)]
t_y0 <- subset(t_y0, t_y0[[y0]] > 0)
att2000 <- read.csv("../data/cleaned/attribute2000.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot00 <- graph_from_data_frame(d = t_y0, directed = TRUE)
E(tot00)$weight <- t_y0[[y0]]
is_directed(tot00) 
length(E(tot00)) == length(E(tot00)$weight)
length(unique(V(tot00)$name)) == gorder(tot00) 
is.character(V(tot00)$name) 
any(is.na(E(tot00)$weight))      
any(!is.finite(E(tot00)$weight)) 
edge_list_t1 <- as_data_frame(tot00, what = "edges")
duplicated_rows_t1 <- duplicated(edge_list_t1[, c("from", "to")])
any(duplicated_rows_t1)  
length(unique(V(tot00)$name))
```

```{r}
attify <- function(n_net, attr_df){
  V(n_net)$iso_o <- V(n_net)$name
  idx <- match(V(n_net)$name, attr_df$iso_o)
  V(n_net)$country <- attr_df$Country[idx]
  V(n_net)$D_log_gdp <- attr_df$D_log_gdp[idx]
  V(n_net)$D_log_gdp_pct <- attr_df$D_log_gdp_pct[idx]
  V(n_net)$log_population <- attr_df$log_population[idx]
  V(n_net)$log_trade_gdp_ratio <- attr_df$log_trade_gdp_ratio[idx]
  V(n_net)$landlocked <- attr_df$landlocked[idx]
  V(n_net)$continent <- attr_df$continent[idx]
  V(n_net)$lat <- attr_df$lat[idx]
  V(n_net)$lon <- attr_df$lon[idx]
  V(n_net)$development <- attr_df$development[idx]
  
  return(n_net)
}

tot00 <- attify(tot00, att2000)
vertex_attr_names(tot00)
```



```{r}
library(wdnet)
class(tot00)
m1 <- igraph_to_wdnet(tot00)
class(m1)
summary(m1)
print(m1, node.attrs = TRUE, edge.attrs = TRUE)
```


```{r}
node_names_t_1 <- m1$node.attr$iso_o 
pageRank_t0 <- centrality(m1, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t0 <- centrality(m1, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t0 <- centrality(m1, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t0 <- centrality(m1, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t01 <- clustcoef(m1, method = "Clemente")$total$localcc
lct_t02 <- clustcoef(m1, method = "Clemente")$out$localcc

centrality_tf0 <- data.frame(iso_o = node_names_t_1, pageRank_total = pageRank_t0, close_total = closeness_t0, outdegree_total = outdegree_t0, indegree_total = indegree_t0, local_clust_tt_total = lct_t01, local_clust_out_total = lct_t02)
head(centrality_tf0)

write.csv(centrality_tf0, "../data/cleaned/network_metrics_total2000.csv")
```

# 2001
```{r}
y1 <- "X2001"   
t_y1 <- t[, c("iso_o", "iso_d", y1)]
t_y1 <- subset(t_y1, t_y1[[y1]] > 0)
att2001 <- read.csv("../data/cleaned/attribute2001.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot01 <- graph_from_data_frame(d = t_y1, directed = TRUE)
E(tot01)$weight <- t_y1[[y1]]
is_directed(tot01) 
length(E(tot01)) == length(E(tot01)$weight)
length(unique(V(tot01)$name)) == gorder(tot01) 
is.character(V(tot01)$name) 
any(is.na(E(tot01)$weight))     
any(!is.finite(E(tot01)$weight)) 
edge_list_t2 <- as_data_frame(tot01, what = "edges")
duplicated_rows_t2 <- duplicated(edge_list_t2[, c("from", "to")])
any(duplicated_rows_t2)  
length(unique(V(tot01)$name))
tot01 <- attify(tot01, att2001)
vertex_attr_names(tot01)
```

```{r}
class(tot01)
m2 <- igraph_to_wdnet(tot01)
class(m2)
summary(m2)
print(m2, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names_t_2 <- m2$node.attr$iso_o 
pageRank_t1 <- centrality(m2, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t1 <- centrality(m2, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t1 <- centrality(m2, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t1 <- centrality(m2, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t11 <- clustcoef(m2, method = "Clemente")$total$localcc
lct_t12 <- clustcoef(m2, method = "Clemente")$out$localcc

centrality_tf1 <- data.frame(iso_o = node_names_t_2, pageRank_total = pageRank_t1, close_total = closeness_t1, outdegree_total = outdegree_t1, indegree_total = indegree_t1, local_clust_tt_total = lct_t11, local_clust_out_total = lct_t12)
head(centrality_tf1)

write.csv(centrality_tf1, "../data/cleaned/network_metrics_total2001.csv")
```


## 2002
```{r}
y2 <- "X2002"   
t_y2 <- t[, c("iso_o", "iso_d", y2)]
t_y2 <- subset(t_y2, t_y2[[y2]] > 0)
att2002 <- read.csv("../data/cleaned/attribute2002.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot02 <- graph_from_data_frame(d = t_y2, directed = TRUE)
E(tot02)$weight <- t_y2[[y2]]
is_directed(tot02) 
length(E(tot02)) == length(E(tot02)$weight)
length(unique(V(tot02)$name)) == gorder(tot02)  
is.character(V(tot02)$name) 
any(is.na(E(tot02)$weight))     
any(!is.finite(E(tot02)$weight)) 
edge_list_t3 <- as_data_frame(tot02, what = "edges")
duplicated_rows_t3 <- duplicated(edge_list_t3[, c("from", "to")])
any(duplicated_rows_t3)  
length(unique(V(tot02)$name))
tot02 <- attify(tot02, att2002)
vertex_attr_names(tot02)
```

```{r}
class(tot02)
m3 <- igraph_to_wdnet(tot02)
class(m3)
summary(m3)
print(m3, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names_t_3 <- m3$node.attr$iso_o 
pageRank_t2 <- centrality(m3, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t2 <- centrality(m3, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t2 <- centrality(m3, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t2 <- centrality(m3, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t21 <- clustcoef(m3, method = "Clemente")$total$localcc
lct_t22 <- clustcoef(m3, method = "Clemente")$out$localcc

centrality_tf2 <- data.frame(iso_o = node_names_t_3, pageRank_total = pageRank_t2, close_total = closeness_t2, outdegree_total = outdegree_t2, indegree_total = indegree_t2, local_clust_tt_total = lct_t21, local_clust_out_total = lct_t22)
head(centrality_tf1)

write.csv(centrality_tf2, "../data/cleaned/network_metrics_total2002.csv")
```


## 2003
```{r}
y3 <- "X2003"   
t_y3 <- t[, c("iso_o", "iso_d", y3)]
t_y3 <- subset(t_y3, t_y3[[y3]] > 0)
att2003 <- read.csv("../data/cleaned/attribute2003.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot03 <- graph_from_data_frame(d = t_y3, directed = TRUE)
E(tot03)$weight <- t_y3[[y3]]
is_directed(tot03) 
length(E(tot03)) == length(E(tot03)$weight)
length(unique(V(tot03)$name)) == gorder(tot03) 
is.character(V(tot03)$name) 
any(is.na(E(tot03)$weight))     
any(!is.finite(E(tot03)$weight))
edge_list_t4 <- as_data_frame(tot03, what = "edges")
duplicated_rows_t4 <- duplicated(edge_list_t4[, c("from", "to")])
any(duplicated_rows_t4)  
length(unique(V(tot03)$name))
tot03 <- attify(tot03, att2003)
vertex_attr_names(tot03)
```
```{r}
class(tot03)
m4 <- igraph_to_wdnet(tot03)
class(m4)
summary(m4)
print(m4, node.attrs = TRUE, edge.attrs = TRUE)
```
```{r}
node_names_t_4 <- m4$node.attr$iso_o 
pageRank_t3 <- centrality(m4, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t3 <- centrality(m4, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t3 <- centrality(m4, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t3 <- centrality(m4, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t31 <- clustcoef(m4, method = "Clemente")$total$localcc
lct_t32 <- clustcoef(m4, method = "Clemente")$out$localcc

centrality_tf3 <- data.frame(iso_o = node_names_t_4, pageRank_total = pageRank_t3, close_total = closeness_t3, outdegree_total = outdegree_t3, indegree_total = indegree_t3,local_clust_tt_total = lct_t31, local_clust_out_total = lct_t32)
head(centrality_tf3)

write.csv(centrality_tf3, "../data/cleaned/network_metrics_total2003.csv")
```

# 2004
```{r}
y4 <- "X2004"   
t_y4 <- t[, c("iso_o", "iso_d", y4)]
t_y4 <- subset(t_y4, t_y4[[y4]] > 0)
att2004 <- read.csv("../data/cleaned/attribute2004.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot04 <- graph_from_data_frame(d = t_y4, directed = TRUE)
E(tot04)$weight <- t_y4[[y4]]
is_directed(tot04) 
length(E(tot04)) == length(E(tot04)$weight)
length(unique(V(tot04)$name)) == gorder(tot04) 
is.character(V(tot04)$name) 
any(is.na(E(tot04)$weight))     
any(!is.finite(E(tot04)$weight)) 
edge_list_t5 <- as_data_frame(tot04, what = "edges")
duplicated_rows_t5 <- duplicated(edge_list_t5[, c("from", "to")])
any(duplicated_rows_t5)
length(unique(V(tot04)$name))
tot04 <- attify(tot04, att2004)
vertex_attr_names(tot04)
```

```{r}
class(tot04)
m5 <- igraph_to_wdnet(tot04)
class(m5)
summary(m5)
print(m5, node.attrs = TRUE, edge.attrs = TRUE)
```
```{r}
node_names_t_5 <- m5$node.attr$iso_o 
pageRank_t4 <- centrality(m5, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t4 <- centrality(m5, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t4 <- centrality(m5, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t4 <- centrality(m5, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t41 <- clustcoef(m5, method = "Clemente")$total$localcc
lct_t42 <- clustcoef(m5, method = "Clemente")$out$localcc

centrality_tf4 <- data.frame(iso_o = node_names_t_5, pageRank_total = pageRank_t4, close_total = closeness_t4, outdegree_total = outdegree_t4, indegree_total = indegree_t4, local_clust_tt_total = lct_t41, local_clust_out_total = lct_t42)
head(centrality_tf4)

write.csv(centrality_tf4, "../data/cleaned/network_metrics_total2004.csv")
```


# 2005
```{r}
y5 <- "X2005"   
t_y5 <- t[, c("iso_o", "iso_d", y5)]
t_y5 <- subset(t_y5, t_y5[[y5]] > 0)
att2005 <- read.csv("../data/cleaned/attribute2005.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot05 <- graph_from_data_frame(d = t_y5, directed = TRUE)
E(tot05)$weight <- t_y5[[y5]]
is_directed(tot05) 
length(E(tot05)) == length(E(tot05)$weight)
length(unique(V(tot05)$name)) == gorder(tot05)  
is.character(V(tot05)$name) 
any(is.na(E(tot05)$weight))      
any(!is.finite(E(tot05)$weight)) 
edge_list_t6 <- as_data_frame(tot05, what = "edges")
duplicated_rows_t6 <- duplicated(edge_list_t6[, c("from", "to")])
any(duplicated_rows_t6)  
length(unique(V(tot05)$name))
tot05 <- attify(tot05, att2005)
vertex_attr_names(tot05)
```

```{r}
class(tot05)
m6 <- igraph_to_wdnet(tot05)
class(m6)
summary(m6)
print(m6, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names_t_6 <- m6$node.attr$iso_o 
pageRank_t5 <- centrality(m6, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t5 <- centrality(m6, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t5 <- centrality(m6, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t5 <- centrality(m6, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t51 <- clustcoef(m6, method = "Clemente")$total$localcc
lct_t52 <- clustcoef(m6, method = "Clemente")$out$localcc

centrality_tf5 <- data.frame(iso_o = node_names_t_6, pageRank_total = pageRank_t5, close_total = closeness_t5, outdegree_total = outdegree_t5, indegree_total = indegree_t5, local_clust_tt_total = lct_t51, local_clust_out_total = lct_t52)
head(centrality_tf5)

write.csv(centrality_tf5, "../data/cleaned/network_metrics_total2005.csv")
```

# 2006
```{r}
y6 <- "X2006"   
t_y6 <- t[, c("iso_o", "iso_d", y6)]
t_y6 <- subset(t_y6, t_y6[[y6]] > 0)
att2006 <- read.csv("../data/cleaned/attribute2006.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot06 <- graph_from_data_frame(d = t_y6, directed = TRUE)
E(tot06)$weight <- t_y6[[y6]]
is_directed(tot06) 
length(E(tot06)) == length(E(tot06)$weight)
length(unique(V(tot06)$name)) == gorder(tot06)  
is.character(V(tot06)$name) 
any(is.na(E(tot06)$weight))      
any(!is.finite(E(tot06)$weight)) 
edge_list_t7 <- as_data_frame(tot06, what = "edges")
duplicated_rows_t7 <- duplicated(edge_list_t7[, c("from", "to")])
any(duplicated_rows_t7)  
length(unique(V(tot06)$name))
tot06 <- attify(tot06, att2006)
vertex_attr_names(tot06)
```

```{r}
class(tot06)
m7 <- igraph_to_wdnet(tot06)
class(m7)
summary(m7)
print(m7, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names_t_7 <- m7$node.attr$iso_o 
pageRank_t6 <- centrality(m7, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t6 <- centrality(m7, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t6 <- centrality(m7, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t6 <- centrality(m7, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t61 <- clustcoef(m7, method = "Clemente")$total$localcc
lct_t62 <- clustcoef(m7, method = "Clemente")$out$localcc

centrality_tf6 <- data.frame(iso_o = node_names_t_7, pageRank_total = pageRank_t6, close_total = closeness_t6, outdegree_total = outdegree_t6, indegree_total = indegree_t6, local_clust_tt_total = lct_t61, local_clust_out_total = lct_t62)
head(centrality_tf6)

write.csv(centrality_tf6, "../data/cleaned/network_metrics_total2006.csv")

```

## 2007
```{r}
y7 <- "X2007"   
t_y7 <- t[, c("iso_o", "iso_d", y7)]
t_y7 <- subset(t_y7, t_y7[[y7]] > 0)
att2007 <- read.csv("../data/cleaned/attribute2007.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot07 <- graph_from_data_frame(d = t_y7, directed = TRUE)
E(tot07)$weight <- t_y7[[y7]]
is_directed(tot07) 
length(E(tot07)) == length(E(tot07)$weight)
length(unique(V(tot07)$name)) == gorder(tot07)  
is.character(V(tot07)$name) 
any(is.na(E(tot07)$weight))      
any(!is.finite(E(tot07)$weight)) 
edge_list_t8 <- as_data_frame(tot07, what = "edges")
duplicated_rows_t8 <- duplicated(edge_list_t8[, c("from", "to")])
any(duplicated_rows_t8)  
length(unique(V(tot07)$name))
tot07 <- attify(tot07, att2007)
vertex_attr_names(tot07)
```

```{r}
class(tot07)
m8 <- igraph_to_wdnet(tot07)
class(m8)
summary(m8)
print(m8, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names_t_8 <- m8$node.attr$iso_o 
pageRank_t7 <- centrality(m8, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t7 <- centrality(m8, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t7 <- centrality(m8, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t7 <- centrality(m8, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t71 <- clustcoef(m8, method = "Clemente")$total$localcc
lct_t72 <- clustcoef(m8, method = "Clemente")$out$localcc

centrality_tf7 <- data.frame(iso_o = node_names_t_8, pageRank_total = pageRank_t7, close_total = closeness_t7, outdegree_total = outdegree_t7, indegree_total = indegree_t7, local_clust_tt_total = lct_t71, local_clust_out_total = lct_t72)
head(centrality_tf7)

write.csv(centrality_tf7, "../data/cleaned/network_metrics_total2007.csv")
```


## 2008
```{r}
y8 <- "X2008"   
t_y8 <- t[, c("iso_o", "iso_d", y8)]
# Filter out edges with zero trade
t_y8 <- subset(t_y8, t_y8[[y8]] > 0)
att2008 <- read.csv("../data/cleaned/attribute2008.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot08 <- graph_from_data_frame(d = t_y8, directed = TRUE)
E(tot08)$weight <- t_y8[[y8]]
is_directed(tot08) 
length(E(tot08)) == length(E(tot08)$weight)
length(unique(V(tot08)$name)) == gorder(tot08)  
is.character(V(tot08)$name) 
any(is.na(E(tot08)$weight))     
any(!is.finite(E(tot08)$weight)) 
edge_list_t9 <- as_data_frame(tot08, what = "edges")
duplicated_rows_t9 <- duplicated(edge_list_t9[, c("from", "to")])
any(duplicated_rows_t9)  # should be FALSE
length(unique(V(tot08)$name))
tot08 <- attify(tot08, att2008)
vertex_attr_names(tot08)
```

```{r}
class(tot08)
m9 <- igraph_to_wdnet(tot08)
class(m9)
summary(m9)
print(m9, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names_t_9 <- m9$node.attr$iso_o 
pageRank_t8 <- centrality(m9, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t8 <- centrality(m9, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t8 <- centrality(m9, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t8 <- centrality(m9, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t81 <- clustcoef(m9, method = "Clemente")$total$localcc
lct_t82 <- clustcoef(m9, method = "Clemente")$out$localcc

centrality_tf8 <- data.frame(iso_o = node_names_t_9, pageRank_total = pageRank_t8, close_total = closeness_t8, outdegree_total = outdegree_t8, indegree_total = indegree_t8,local_clust_tt_total = lct_t81, local_clust_out_total = lct_t82)
head(centrality_tf8)

write.csv(centrality_tf8, "../data/cleaned/network_metrics_total2008.csv")
```


## 2009
```{r}
y9 <- "X2009"   
t_y9 <- t[, c("iso_o", "iso_d", y9)]
t_y9 <- subset(t_y9, t_y9[[y9]] > 0)
att2009 <- read.csv("../data/cleaned/attribute2009.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot09 <- graph_from_data_frame(d = t_y9, directed = TRUE)
E(tot09)$weight <- t_y9[[y9]]
is_directed(tot09) 
length(E(tot09)) == length(E(tot09)$weight)
length(unique(V(tot09)$name)) == gorder(tot09)  
is.character(V(tot09)$name) 
any(is.na(E(tot09)$weight))      
any(!is.finite(E(tot09)$weight)) 
edge_list_t10 <- as_data_frame(tot09, what = "edges")
duplicated_rows_t10 <- duplicated(edge_list_t10[, c("from", "to")])
any(duplicated_rows_t10)  
length(unique(V(tot09)$name))
tot09 <- attify(tot09, att2009)
vertex_attr_names(tot09)
```

```{r}
class(tot09)
m10 <- igraph_to_wdnet(tot09)
class(m10)
summary(m10)
print(m10, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names_t_10 <- m10$node.attr$iso_o 
pageRank_t9 <- centrality(m10, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t9 <- centrality(m10, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t9 <- centrality(m10, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t9 <- centrality(m10, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t91 <- clustcoef(m10, method = "Clemente")$total$localcc
lct_t92 <- clustcoef(m10, method = "Clemente")$out$localcc

centrality_tf9 <- data.frame(iso_o = node_names_t_10, pageRank_total = pageRank_t9, close_total = closeness_t9, outdegree_total = outdegree_t9, indegree_total = indegree_t9,local_clust_tt_total = lct_t91, local_clust_out_total = lct_t92)
head(centrality_tf9)

write.csv(centrality_tf9, "../data/cleaned/network_metrics_total2009.csv")
```


## 2010
```{r}
y10 <- "X2010"   
t_y10 <- t[, c("iso_o", "iso_d", y10)]
# Filter out edges with zero trade
t_y10 <- subset(t_y10, t_y10[[y10]] > 0)
att2010 <- read.csv("../data/cleaned/attribute2010.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot10 <- graph_from_data_frame(d = t_y10, directed = TRUE)
E(tot10)$weight <- t_y10[[y10]]
is_directed(tot10) 
length(E(tot10)) == length(E(tot10)$weight)
length(unique(V(tot10)$name)) == gorder(tot10)  # should be TRUE
is.character(V(tot10)$name) 
any(is.na(E(tot10)$weight))      # should be FALSE
any(!is.finite(E(tot10)$weight)) # should be FALSE
edge_list_t11 <- as_data_frame(tot10, what = "edges")
duplicated_rows_t11 <- duplicated(edge_list_t11[, c("from", "to")])
any(duplicated_rows_t11)  # should be FALSE
length(unique(V(tot10)$name))
tot10 <- attify(tot10, att2010)
vertex_attr_names(tot10)
```

```{r}
class(tot10)
m11 <- igraph_to_wdnet(tot10)
class(m11)
summary(m11)
print(m11, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names_t_11 <- m11$node.attr$iso_o 
pageRank_t10 <- centrality(m11, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t10 <- centrality(m11, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t10 <- centrality(m11, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t10 <- centrality(m11, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t101 <- clustcoef(m11, method = "Clemente")$total$localcc
lct_t102 <- clustcoef(m11, method = "Clemente")$out$localcc

centrality_tf10 <- data.frame(iso_o = node_names_t_11, pageRank_total = pageRank_t10, close_total = closeness_t10, outdegree_total = outdegree_t10, indegree_total = indegree_t10, local_clust_tt_total = lct_t101, local_clust_out_total = lct_t102)
head(centrality_tf10)

write.csv(centrality_tf10, "../data/cleaned/network_metrics_total2010.csv")
```

## 2011
```{r}
y11 <- "X2011"   
t_y11 <- t[, c("iso_o", "iso_d", y11)]
# Filter out edges with zero trade
t_y11 <- subset(t_y11, t_y11[[y11]] > 0)
att2011 <- read.csv("../data/cleaned/attribute2011.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot11 <- graph_from_data_frame(d = t_y11, directed = TRUE)
E(tot11)$weight <- t_y11[[y11]]
is_directed(tot11) 
length(E(tot11)) == length(E(tot11)$weight)
length(unique(V(tot11)$name)) == gorder(tot11)  # should be TRUE
is.character(V(tot11)$name) 
any(is.na(E(tot11)$weight))      # should be FALSE
any(!is.finite(E(tot11)$weight)) # should be FALSE
edge_list_t12 <- as_data_frame(tot11, what = "edges")
duplicated_rows_t12 <- duplicated(edge_list_t12[, c("from", "to")])
any(duplicated_rows_t12)  # should be FALSE
length(unique(V(tot11)$name))
tot11 <- attify(tot11, att2011)
vertex_attr_names(tot11)
```

```{r}
class(tot11)
m12 <- igraph_to_wdnet(tot11)
class(m12)
summary(m12)
print(m12, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names_t_12 <- m12$node.attr$iso_o 
pageRank_t11 <- centrality(m12, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t11 <- centrality(m12, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t11 <- centrality(m12, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t11 <- centrality(m12, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t111 <- clustcoef(m12, method = "Clemente")$total$localcc
lct_t112 <- clustcoef(m12, method = "Clemente")$out$localcc

centrality_tf11 <- data.frame(iso_o = node_names_t_12, pageRank_total = pageRank_t11, close_total = closeness_t11, outdegree_total = outdegree_t11, indegree_total = indegree_t11, local_clust_tt_total = lct_t111, local_clust_out_total = lct_t112)
head(centrality_tf11)

write.csv(centrality_tf11, "../data/cleaned/network_metrics_total2011.csv")
```


## 2012
```{r}
y12 <- "X2012"   
t_y12 <- t[, c("iso_o", "iso_d", y12)]
t_y12 <- subset(t_y12, t_y12[[y12]] > 0)
att2012 <- read.csv("../data/cleaned/attribute2012.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot12 <- graph_from_data_frame(d = t_y12, directed = TRUE)
E(tot12)$weight <- t_y12[[y12]]
is_directed(tot12) 
length(E(tot12)) == length(E(tot12)$weight)
length(unique(V(tot12)$name)) == gorder(tot12)  
is.character(V(tot12)$name) 
any(is.na(E(tot12)$weight))      
any(!is.finite(E(tot12)$weight)) 
edge_list_t13 <- as_data_frame(tot12, what = "edges")
duplicated_rows_t13 <- duplicated(edge_list_t13[, c("from", "to")])
any(duplicated_rows_t13)  
length(unique(V(tot12)$name))
tot12 <- attify(tot12, att2012)
vertex_attr_names(tot12)
```

```{r}
class(tot12)
m13 <- igraph_to_wdnet(tot12)
class(m13)
summary(m13)
print(m13, node.attrs = TRUE, edge.attrs = TRUE)

```

```{r}
node_names_t_13 <- m13$node.attr$iso_o 
pageRank_t12 <- centrality(m13, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t12 <- centrality(m13, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t12 <- centrality(m13, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t12 <- centrality(m13, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t121 <- clustcoef(m13, method = "Clemente")$total$localcc
lct_t122 <- clustcoef(m13, method = "Clemente")$out$localcc

centrality_tf12 <- data.frame(iso_o = node_names_t_13, pageRank_total = pageRank_t12, close_total = closeness_t12, outdegree_total = outdegree_t12, indegree_total = indegree_t12,local_clust_tt_total = lct_t121, local_clust_out_total = lct_t122)
head(centrality_tf12)

write.csv(centrality_tf12, "../data/cleaned/network_metrics_total2012.csv")
```

## 2013
```{r}
y13 <- "X2013"   
t_y13 <- t[, c("iso_o", "iso_d", y13)]
t_y13 <- subset(t_y13, t_y13[[y13]] > 0)
att2013 <- read.csv("../data/cleaned/attribute2013.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot13 <- graph_from_data_frame(d = t_y13, directed = TRUE)
E(tot13)$weight <- t_y13[[y13]]
is_directed(tot13) 
length(E(tot13)) == length(E(tot13)$weight)
length(unique(V(tot13)$name)) == gorder(tot13)  
is.character(V(tot13)$name) 
any(is.na(E(tot13)$weight))      
any(!is.finite(E(tot13)$weight)) 
edge_list_t14 <- as_data_frame(tot13, what = "edges")
duplicated_rows_t14 <- duplicated(edge_list_t14[, c("from", "to")])
any(duplicated_rows_t14)  
length(unique(V(tot13)$name))
tot13 <- attify(tot13, att2013)
vertex_attr_names(tot13)
```

```{r}
class(tot13)
m14 <- igraph_to_wdnet(tot13)
class(m14)
summary(m14)
print(m14, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names_t_14 <- m14$node.attr$iso_o 
pageRank_t13 <- centrality(m14, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t13 <- centrality(m14, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t13 <- centrality(m14, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t13 <- centrality(m14, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t131 <- clustcoef(m14, method = "Clemente")$total$localcc
lct_t132 <- clustcoef(m14, method = "Clemente")$out$localcc

centrality_tf13 <- data.frame(iso_o = node_names_t_14, pageRank_total = pageRank_t13, close_total = closeness_t13, outdegree_total = outdegree_t13, indegree_total = indegree_t13, local_clust_tt_total = lct_t131, local_clust_out_total = lct_t132)
head(centrality_tf13)

write.csv(centrality_tf13, "../data/cleaned/network_metrics_total2013.csv")
```


## 2014
```{r}
y14 <- "X2014"   
t_y14 <- t[, c("iso_o", "iso_d", y14)]
t_y14 <- subset(t_y14, t_y14[[y14]] > 0)
att2014 <- read.csv("../data/cleaned/attribute2014.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot14 <- graph_from_data_frame(d = t_y14, directed = TRUE)
E(tot14)$weight <- t_y14[[y14]]
is_directed(tot14) 
length(E(tot14)) == length(E(tot14)$weight)
length(unique(V(tot14)$name)) == gorder(tot14)  
is.character(V(tot14)$name) 
any(is.na(E(tot14)$weight))      
any(!is.finite(E(tot14)$weight)) 
edge_list_t15 <- as_data_frame(tot14, what = "edges")
duplicated_rows_t15 <- duplicated(edge_list_t15[, c("from", "to")])
any(duplicated_rows_t15)  
length(unique(V(tot14)$name))
tot14 <- attify(tot14, att2014)
vertex_attr_names(tot14)
```

```{r}
class(tot14)
m15 <- igraph_to_wdnet(tot14)
class(m15)
summary(m15)
print(m15, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names_t_15 <- m15$node.attr$iso_o 
pageRank_t14 <- centrality(m15, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t14 <- centrality(m15, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t14 <- centrality(m15, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t14 <- centrality(m15, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t141 <- clustcoef(m15, method = "Clemente")$total$localcc
lct_t142 <- clustcoef(m15, method = "Clemente")$out$localcc

centrality_tf14 <- data.frame(iso_o = node_names_t_15, pageRank_total = pageRank_t14, close_total = closeness_t14, outdegree_total = outdegree_t14, indegree_total = indegree_t14,local_clust_tt_total = lct_t141, local_clust_out_total = lct_t142)
head(centrality_tf14)

write.csv(centrality_tf14, "../data/cleaned/network_metrics_total2014.csv")
```

## 2015
```{r}
y15 <- "X2015"   
t_y15 <- t[, c("iso_o", "iso_d", y15)]
t_y15 <- subset(t_y15, t_y15[[y15]] > 0)
att2015 <- read.csv("../data/cleaned/attribute2015.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot15 <- graph_from_data_frame(d = t_y15, directed = TRUE)
E(tot15)$weight <- t_y15[[y15]]
is_directed(tot15) 
length(E(tot15)) == length(E(tot15)$weight)
length(unique(V(tot15)$name)) == gorder(tot15)  
is.character(V(tot15)$name) 
any(is.na(E(tot15)$weight))      
any(!is.finite(E(tot15)$weight)) 
edge_list_t16 <- as_data_frame(tot15, what = "edges")
duplicated_rows_t16 <- duplicated(edge_list_t16[, c("from", "to")])
any(duplicated_rows_t16) 
length(unique(V(tot15)$name))
tot15 <- attify(tot15, att2015)
vertex_attr_names(tot15)
```

```{r}
class(tot15)
m16 <- igraph_to_wdnet(tot15)
class(m16)
summary(m16)
print(m16, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names_t_16 <- m16$node.attr$iso_o 
pageRank_t15 <- centrality(m16, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t15 <- centrality(m16, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t15 <- centrality(m16, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t15 <- centrality(m16, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t151 <- clustcoef(m16, method = "Clemente")$total$localcc
lct_t152 <- clustcoef(m16, method = "Clemente")$out$localcc

centrality_tf15 <- data.frame(iso_o = node_names_t_16, pageRank_total = pageRank_t15, close_total = closeness_t15, outdegree_total = outdegree_t15, indegree_total = indegree_t15, local_clust_tt_total = lct_t151, local_clust_out_total = lct_t152)
head(centrality_tf15)

write.csv(centrality_tf15, "../data/cleaned/network_metrics_total2015.csv")
```


# 2016
```{r}
y16 <- "X2016"   
t_y16 <- t[, c("iso_o", "iso_d", y16)]
t_y16 <- subset(t_y16, t_y16[[y16]] > 0)
att2016 <- read.csv("../data/cleaned/attribute2016.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot16 <- graph_from_data_frame(d = t_y16, directed = TRUE)
E(tot16)$weight <- t_y16[[y16]]
is_directed(tot16) 
length(E(tot16)) == length(E(tot16)$weight)
length(unique(V(tot16)$name)) == gorder(tot16)  
is.character(V(tot16)$name) 
any(is.na(E(tot16)$weight))      
any(!is.finite(E(tot16)$weight)) 
edge_list_t17 <- as_data_frame(tot16, what = "edges")
duplicated_rows_t17 <- duplicated(edge_list_t17[, c("from", "to")])
any(duplicated_rows_t17)  
length(unique(V(tot16)$name))
tot16 <- attify(tot16, att2016)
vertex_attr_names(tot16)
```

```{r}
class(tot16)
m17 <- igraph_to_wdnet(tot16)
class(m17)
summary(m17)
print(m17, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names_t_17 <- m17$node.attr$iso_o 
pageRank_t16 <- centrality(m17, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t16 <- centrality(m17, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t16 <- centrality(m17, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t16 <- centrality(m17, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t161 <- clustcoef(m17, method = "Clemente")$total$localcc
lct_t162 <- clustcoef(m17, method = "Clemente")$out$localcc

centrality_tf16 <- data.frame(iso_o = node_names_t_17, pageRank_total = pageRank_t16, close_total = closeness_t16, outdegree_total = outdegree_t16, indegree_total = indegree_t16, local_clust_tt_total = lct_t161, local_clust_out_total = lct_t162)
head(centrality_tf16)

write.csv(centrality_tf16, "../data/cleaned/network_metrics_total2016.csv")
```

## 2017
```{r}
y17 <- "X2017"   
t_y17 <- t[, c("iso_o", "iso_d", y17)]
t_y17 <- subset(t_y17, t_y17[[y17]] > 0)
att2017 <- read.csv("../data/cleaned/attribute2017.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot17 <- graph_from_data_frame(d = t_y17, directed = TRUE)
E(tot17)$weight <- t_y17[[y17]]
is_directed(tot17) 
length(E(tot17)) == length(E(tot17)$weight)
length(unique(V(tot17)$name)) == gorder(tot17)  
is.character(V(tot17)$name) 
any(is.na(E(tot17)$weight))     
any(!is.finite(E(tot17)$weight))

edge_list_t18 <- as_data_frame(tot17, what = "edges")
duplicated_rows_t18 <- duplicated(edge_list_t18[, c("from", "to")])
any(duplicated_rows_t18)  
length(unique(V(tot17)$name))
tot17 <- attify(tot17, att2017)
vertex_attr_names(tot17)
```

```{r}
class(tot17)
m18 <- igraph_to_wdnet(tot17)
class(m18)
summary(m18)
print(m18, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names_t_18 <- m18$node.attr$iso_o 
pageRank_t17 <- centrality(m18, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t17 <- centrality(m18, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t17 <- centrality(m18, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t17 <- centrality(m18, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t171 <- clustcoef(m18, method = "Clemente")$total$localcc
lct_t172 <- clustcoef(m18, method = "Clemente")$out$localcc

centrality_tf17 <- data.frame(iso_o = node_names_t_18, pageRank_total = pageRank_t17, close_total = closeness_t17, outdegree_total = outdegree_t17, indegree_total = indegree_t17, local_clust_tt_total = lct_t171, local_clust_out_total = lct_t172)
head(centrality_tf17)

write.csv(centrality_tf17, "../data/cleaned/network_metrics_total2017.csv")
```

## 2018
```{r}
y18 <- "X2018"   
t_y18 <- t[, c("iso_o", "iso_d", y18)]
t_y18 <- subset(t_y18, t_y18[[y18]] > 0)
att2018 <- read.csv("../data/cleaned/attribute2018.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot18 <- graph_from_data_frame(d = t_y18, directed = TRUE)
E(tot18)$weight <- t_y18[[y18]]
is_directed(tot18) 
length(E(tot18)) == length(E(tot18)$weight)
length(unique(V(tot18)$name)) == gorder(tot18)  
is.character(V(tot18)$name) 
any(is.na(E(tot18)$weight))      
any(!is.finite(E(tot18)$weight))

edge_list_t19 <- as_data_frame(tot18, what = "edges")
duplicated_rows_t19 <- duplicated(edge_list_t19[, c("from", "to")])
any(duplicated_rows_t19)  # should be FALSE
length(unique(V(tot18)$name))
tot18 <- attify(tot18, att2018)
vertex_attr_names(tot18)
```

```{r}
class(tot18)
m19<- igraph_to_wdnet(tot18)
class(m19)
summary(m19)
vertex_attr_names(tot18)
print(m19, node.attrs= TRUE, edge.attrs= TRUE)
```

```{r}
node_names_t_19 <- m19$node.attr$iso_o 
pageRank_t18 <- centrality(m19, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t18 <- centrality(m19, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t18 <- centrality(m19, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t18 <- centrality(m19, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t181 <- clustcoef(m19, method = "Clemente")$total$localcc
lct_t182 <- clustcoef(m19, method = "Clemente")$out$localcc

centrality_tf18 <- data.frame(iso_o = node_names_t_19, pageRank_total = pageRank_t18, close_total = closeness_t18, outdegree_total = outdegree_t18, indegree_total = indegree_t18, local_clust_tt_total = lct_t181, local_clust_out_total = lct_t182)
head(centrality_tf18)

write.csv(centrality_tf18, "../data/cleaned/network_metrics_total2018.csv")
```

## 2019
```{r}
y19 <- "X2019"   
t_y19 <- t[, c("iso_o", "iso_d", y19)]
t_y19 <- subset(t_y19, t_y19[[y19]] > 0)
att2019 <- read.csv("../data/cleaned/attribute2019.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot19 <- graph_from_data_frame(d = t_y19, directed = TRUE)
E(tot19)$weight <- t_y19[[y19]]
is_directed(tot19) 
length(E(tot19)) == length(E(tot19)$weight)
length(unique(V(tot19)$name)) == gorder(tot19)  
is.character(V(tot19)$name) 
any(is.na(E(tot19)$weight))      
any(!is.finite(E(tot19)$weight)) 

edge_list_t20 <- as_data_frame(tot19, what = "edges")
duplicated_rows_t20 <- duplicated(edge_list_t20[, c("from", "to")])
any(duplicated_rows_t20)  # should be FALSE
length(unique(V(tot19)$name))
tot19 <- attify(tot19, att2019)
vertex_attr_names(tot19)
```

```{r}
class(tot19)
m20<- igraph_to_wdnet(tot19)
class(m20)
summary(m20)
vertex_attr_names(tot19)
print(m20, node.attrs= TRUE, edge.attrs= TRUE)
```

```{r}
node_names_t_20 <- m20$node.attr$iso_o 
pageRank_t19 <- centrality(m20, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t19 <- centrality(m20, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t19 <- centrality(m20, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t19 <- centrality(m20, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t191 <- clustcoef(m20, method = "Clemente")$total$localcc
lct_t192 <- clustcoef(m20, method = "Clemente")$out$localcc

centrality_tf19 <- data.frame(iso_o = node_names_t_20, pageRank_total = pageRank_t19, close_total = closeness_t19, outdegree_total = outdegree_t19, indegree_total = indegree_t19, local_clust_tt_total = lct_t191, local_clust_out_total = lct_t192)
head(centrality_tf19)

write.csv(centrality_tf19, "../data/cleaned/network_metrics_total2019.csv")
```

# 2020
```{r}
y20 <- "X2020"   
t_y20 <- t[, c("iso_o", "iso_d", y20)]
t_y20 <- subset(t_y20, t_y20[[y20]] > 0)
att2020 <- read.csv("../data/cleaned/attribute2020.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot20 <- graph_from_data_frame(d = t_y20, directed = TRUE)
E(tot20)$weight <- t_y20[[y20]]
is_directed(tot20) 
length(E(tot20)) == length(E(tot20)$weight)
length(unique(V(tot20)$name)) == gorder(tot20)  
is.character(V(tot20)$name) 
any(is.na(E(tot20)$weight))     
any(!is.finite(E(tot20)$weight)) 

edge_list_t21 <- as_data_frame(tot20, what = "edges")
duplicated_rows_t21 <- duplicated(edge_list_t21[, c("from", "to")])
any(duplicated_rows_t21)  
length(unique(V(tot20)$name))
tot20 <- attify(tot20, att2020)
vertex_attr_names(tot20)
```

```{r}
class(tot20)
m21<- igraph_to_wdnet(tot20)
class(m21)
summary(m21)
vertex_attr_names(tot20)
print(m21, node.attrs= TRUE, edge.attrs= TRUE)
```

```{r}
node_names_t_21 <- m21$node.attr$iso_o 
pageRank_t20 <- centrality(m21, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t20 <- centrality(m21, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t20 <- centrality(m21, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t20 <- centrality(m21, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t201 <- clustcoef(m21, method = "Clemente")$total$localcc
lct_t202 <- clustcoef(m21, method = "Clemente")$out$localcc

centrality_tf20 <- data.frame(iso_o = node_names_t_21, pageRank_total = pageRank_t20, close_total = closeness_t20, outdegree_total = outdegree_t20, indegree_total = indegree_t20, local_clust_tt_total = lct_t201, local_clust_out_total = lct_t202)
head(centrality_tf20)

write.csv(centrality_tf20, "../data/cleaned/network_metrics_total2020.csv")
```

# 2021
```{r}
y21 <- "X2021"   
t_y21 <- t[, c("iso_o", "iso_d", y21)]
t_y21 <- subset(t_y21, t_y21[[y21]] > 0)
att2021 <- read.csv("../data/cleaned/attribute2021.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot21 <- graph_from_data_frame(d = t_y21, directed = TRUE)
E(tot21)$weight <- t_y21[[y21]]
is_directed(tot21) 
length(E(tot21)) == length(E(tot21)$weight)
length(unique(V(tot21)$name)) == gorder(tot21)  
is.character(V(tot21)$name) 
any(is.na(E(tot21)$weight))      
any(!is.finite(E(tot21)$weight)) 

edge_list_t22 <- as_data_frame(tot21, what = "edges")
duplicated_rows_t22 <- duplicated(edge_list_t22[, c("from", "to")])
any(duplicated_rows_t22)  # should be FALSE
length(unique(V(tot21)$name))
tot21 <- attify(tot21, att2021)
vertex_attr_names(tot21)
```

```{r}
class(tot21)
m22 <- igraph_to_wdnet(tot21)
class(m22)
summary(m22)
vertex_attr_names(tot21)
print(m22, node.attrs= TRUE, edge.attrs= TRUE)
```

```{r}
node_names_t_22 <- m22$node.attr$iso_o 
pageRank_t21 <- centrality(m22, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t21 <- centrality(m22, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t21 <- centrality(m22, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t21 <- centrality(m22, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t211 <- clustcoef(m22, method = "Clemente")$total$localcc
lct_t212 <- clustcoef(m22, method = "Clemente")$out$localcc

centrality_tf21 <- data.frame(iso_o = node_names_t_22, pageRank_total = pageRank_t21, close_total = closeness_t21, outdegree_total = outdegree_t21, indegree_total = indegree_t21, local_clust_tt_total = lct_t211, local_clust_out_total = lct_t212)
head(centrality_tf21)

write.csv(centrality_tf21, "../data/cleaned/network_metrics_total2021.csv")
```

# 2022
```{r}
y22 <- "X2022"   
t_y22 <- t[, c("iso_o", "iso_d", y22)]
t_y22 <- subset(t_y22, t_y22[[y22]] > 0)
att2022 <- read.csv("../data/cleaned/attribute2022.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot22 <- graph_from_data_frame(d = t_y22, directed = TRUE)
E(tot22)$weight <- t_y22[[y22]]
is_directed(tot22) 
length(E(tot22)) == length(E(tot22)$weight)
length(unique(V(tot22)$name)) == gorder(tot22) 
is.character(V(tot22)$name) 
any(is.na(E(tot22)$weight))      
any(!is.finite(E(tot22)$weight)) 

edge_list_t23 <- as_data_frame(tot22, what = "edges")
duplicated_rows_t23 <- duplicated(edge_list_t23[, c("from", "to")])
any(duplicated_rows_t23)  
length(unique(V(tot22)$name))
tot22 <- attify(tot22, att2022)
vertex_attr_names(tot22)
```

```{r}
class(tot22)
m23 <- igraph_to_wdnet(tot22)
class(m23)
summary(m23)
vertex_attr_names(tot22)
print(m23, node.attrs= TRUE, edge.attrs= TRUE)
```

```{r}
node_names_t_23 <- m23$node.attr$iso_o 
pageRank_t22 <- centrality(m23, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t22 <- centrality(m23, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t22 <- centrality(m23, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t22 <- centrality(m23, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t221 <- clustcoef(m23, method = "Clemente")$total$localcc
lct_t222 <- clustcoef(m23, method = "Clemente")$out$localcc

centrality_tf22 <- data.frame(iso_o = node_names_t_23, pageRank_total = pageRank_t22, close_total = closeness_t22, outdegree_total = outdegree_t22, indegree_total = indegree_t22, local_clust_tt_total = lct_t221, local_clust_out_total = lct_t222)
head(centrality_tf22)

write.csv(centrality_tf22, "../data/cleaned/network_metrics_total2022.csv")
```

#2023
```{r}
y23 <- "X2023"   
t_y23 <- t[, c("iso_o", "iso_d", y23)]
t_y23 <- subset(t_y23, t_y23[[y23]] > 0)
att2023 <- read.csv("../data/cleaned/attribute2023.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot23 <- graph_from_data_frame(d = t_y23, directed = TRUE)
E(tot23)$weight <- t_y23[[y23]]
is_directed(tot23) 
length(E(tot23)) == length(E(tot23)$weight)
length(unique(V(tot23)$name)) == gorder(tot23)  
is.character(V(tot23)$name) 
any(is.na(E(tot23)$weight))      
any(!is.finite(E(tot23)$weight))

edge_list_t24 <- as_data_frame(tot23, what = "edges")
duplicated_rows_t24 <- duplicated(edge_list_t24[, c("from", "to")])
any(duplicated_rows_t23)  # should be FALSE
length(unique(V(tot23)$name))
tot23 <- attify(tot23, att2023)
vertex_attr_names(tot23)
```

```{r}
class(tot23)
m24 <- igraph_to_wdnet(tot23)
class(m24)
summary(m24)
vertex_attr_names(tot23)
print(m24, node.attrs= TRUE, edge.attrs= TRUE)
```

```{r}
node_names_t_24 <- m24$node.attr$iso_o 
pageRank_t23 <- centrality(m24, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness_t23 <- centrality(m24, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree_t23 <- centrality(m24, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree_t23 <- centrality(m24, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct_t231 <- clustcoef(m24, method = "Clemente")$total$localcc
lct_t232 <- clustcoef(m24, method = "Clemente")$out$localcc

centrality_tf23 <- data.frame(iso_o = node_names_t_24, pageRank_total = pageRank_t23, close_total = closeness_t23, outdegree_total = outdegree_t23, indegree_total = indegree_t23, local_clust_tt_total = lct_t231, local_clust_out_total = lct_t232)
head(centrality_tf23)

write.csv(centrality_tf23, "../data/cleaned/network_metrics_total2023.csv")
```


```{r}
metric_time_total <- data.frame(TIME_PERIOD = c(2000, 2001, 2002, 2003, 2004, 2005, 2006, 2007, 2008,
                                          2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017,
                                          2018, 2019, 2020, 2021, 2022, 2023),
                    Global_CC_Cl_total = c(clustcoef(m1, method ="Clemente")$total$globalcc,
                                         clustcoef(m2, method = "Clemente")$total$globalcc,
                                         clustcoef(m3, method = "Clemente")$total$globalcc,
                                         clustcoef(m4, method = "Clemente")$total$globalcc,
                                         clustcoef(m5, method = "Clemente")$total$globalcc,
                                         clustcoef(m6, method = "Clemente")$total$globalcc,
                                         clustcoef(m7, method ="Clemente")$total$globalcc,
                                         clustcoef(m8, method = "Clemente")$total$globalcc,
                                         clustcoef(m9, method = "Clemente")$total$globalcc,
                                         clustcoef(m10, method = "Clemente")$total$globalcc,
                                         clustcoef(m11, method = "Clemente")$total$globalcc,
                                         clustcoef(m12, method = "Clemente")$total$globalcc,
                                         clustcoef(m13, method ="Clemente")$total$globalcc,
                                         clustcoef(m14, method = "Clemente")$total$globalcc,
                                         clustcoef(m15, method = "Clemente")$total$globalcc,
                                         clustcoef(m16, method = "Clemente")$total$globalcc,
                                         clustcoef(m17, method = "Clemente")$total$globalcc,
                                         clustcoef(m18, method = "Clemente")$total$globalcc,
                                         clustcoef(m19, method ="Clemente")$total$globalcc,
                                         clustcoef(m20, method = "Clemente")$total$globalcc,
                                         clustcoef(m21, method = "Clemente")$total$globalcc,
                                         clustcoef(m22, method = "Clemente")$total$globalcc,
                                         clustcoef(m23, method = "Clemente")$total$globalcc,
                                         clustcoef(m24, method = "Clemente")$total$globalcc),
                    Global_CC_Fg_total = c(clustcoef(m1, method = "Clemente")$out$globalcc,
                                         clustcoef(m2, method = "Clemente")$out$globalcc,
                                         clustcoef(m3, method = "Clemente")$out$globalcc,
                                         clustcoef(m4, method = "Clemente")$out$globalcc,
                                         clustcoef(m5, method = "Clemente")$out$globalcc,
                                         clustcoef(m6, method = "Clemente")$out$globalcc,
                                         clustcoef(m7, method = "Clemente")$out$globalcc,
                                         clustcoef(m8, method = "Clemente")$out$globalcc,
                                         clustcoef(m9, method = "Clemente")$out$globalcc,
                                         clustcoef(m10, method = "Clemente")$out$globalcc,
                                         clustcoef(m11, method = "Clemente")$out$globalcc,
                                         clustcoef(m12, method = "Clemente")$out$globalcc,
                                         clustcoef(m13, method = "Clemente")$out$globalcc,
                                         clustcoef(m14, method = "Clemente")$out$globalcc,
                                         clustcoef(m15, method = "Clemente")$out$globalcc,
                                         clustcoef(m16, method = "Clemente")$out$globalcc,
                                         clustcoef(m17, method = "Clemente")$out$globalcc,
                                         clustcoef(m18, method = "Clemente")$out$globalcc,
                                         clustcoef(m19, method = "Clemente")$out$globalcc,
                                         clustcoef(m20, method = "Clemente")$out$globalcc,
                                         clustcoef(m21, method = "Clemente")$out$globalcc,
                                         clustcoef(m22, method = "Clemente")$out$globalcc,
                                         clustcoef(m23, method = "Clemente")$out$globalcc,
                                         clustcoef(m24, method = "Clemente")$out$globalcc),
                   Avg_CC_Cl_total = c(mean(clustcoef(m1, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m2, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m3, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m4, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m5, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m6, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m7, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m8, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m9, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m10, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m11, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m12, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m13, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m14, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m15, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m16, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m17, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m18, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m19, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m20, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m21, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m22, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m23, method = "Clemente")$total$localcc),
                                      mean(clustcoef(m24, method = "Clemente")$total$localcc)),
                   Avg_CC_Fg_total = c(mean(clustcoef(m1, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m2, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m3, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m4, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m5, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m6, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m7, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m8, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m9, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m10, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m11, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m12, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m13, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m14, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m15, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m16, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m17, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m18, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m19, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m20, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m21, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m21, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m23, method = "Clemente")$out$localcc),
                                      mean(clustcoef(m24, method = "Clemente")$out$localcc)),
                  assortcoef_total = c(assortcoef(m1), 
                                      assortcoef(m2), 
                                      assortcoef(m3), 
                                      assortcoef(m4),
                                      assortcoef(m5), 
                                      assortcoef(m6), 
                                      assortcoef(m7), 
                                      assortcoef(m8),
                                      assortcoef(m9), 
                                      assortcoef(m10), 
                                      assortcoef(m11), 
                                      assortcoef(m12),
                                      assortcoef(m13), 
                                      assortcoef(m14), 
                                      assortcoef(m15), 
                                      assortcoef(m16),
                                      assortcoef(m17), 
                                      assortcoef(m18), 
                                      assortcoef(m19), 
                                      assortcoef(m20),
                                      assortcoef(m21), 
                                      assortcoef(m22), 
                                      assortcoef(m23), 
                                      assortcoef(m24)))

```

```{r}
metric_time_total
```


```{r}
write.csv(metric_time_total, "../data/cleaned/network_metrics_timeseries_total.csv")
```


