---
title: "STERGM on unique cultural goods trade"
author: "Author"
date: "2025-06-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages("pacman")
#pacman::p_unload(pacman::p_loaded(), character.only = TRUE) 
```
# Steps of STERGM:
1. Loading `network`, `igraph`, `intergraph` and `reshape2` packages
2. Making the distance network as a network object with edge weights as distances
3. Making four adjacency matrices with binary values for common colonizer, colonizer, common language, and contiguity
4. Defining a function to add node attributes to the networks
5. Loading the edgelist of unique cultural goods trade, and making 29 network objects for 29 consecutive years following the steps,     
    + Keeping only the pairs with positive weights
    + Subsetting the dataframe with only 'iso_o' and 'iso_d' column
    + Making an igraph object and assigning node attributes from the function created in the third step
    + Making a function for repeating the above four steps for all the years.
6. Converting all 24 igraph objects to network objects
7. Checking the node attributes for all of the networks
8. Making RTA adjacency matrices for all 29 years and converting it to a networkDynamic object. 
10. Running STERGM, calculating odds ratios, standard errors, and confidence intervals, and plotting goodness of fit and MCMC statistics


```{r}
library(network)
library(igraph)
library(intergraph)
library(reshape2)
```

```{r}
lang <- read.csv("../data/cleaned/language_edgelist.csv",stringsAsFactors = FALSE)
lang_mat <- acast(lang, iso_o ~ iso_d, value.var = "comlang_off", fill = 0)

contiguity <- read.csv("../data/cleaned/contiguity_edgelist.csv",stringsAsFactors = FALSE)
contig_mat <- acast(contiguity, iso_o ~ iso_d, value.var = "contig", fill = 0)

common_col <- read.csv("../data/cleaned/comcol_edgelist.csv",stringsAsFactors = FALSE)
col_mat <- acast(common_col, iso_o ~ iso_d, value.var = "comcol", fill = 0)

colonizer <- read.csv("../data/cleaned/colonizer_edgelist.csv",stringsAsFactors = FALSE)
colony <- acast(colonizer, iso_o ~ iso_d, value.var = "colony", fill = 0)

dist_1 <- read.csv("../data/cleaned/distance_edgelist.csv",stringsAsFactors = FALSE)

#sd(log(dist_1$dist))
sd(log(dist_1$log_dist))
```
```{r}
dist_net <- network(dist_1[, c("iso_o", "iso_d")], directed = TRUE, matrix.type = "edgelist", 
loops = FALSE)

# assigning the log_distance as edge attributes
set.edge.value(dist_net, "log_dist", dist_1$log_dist)
```

```{r}
#summary(dist_net)
#get.edge.value(dist_net, "log_dist")
```

# Unique culture Goods trade edgelist
```{r}
u <- read.csv("../data/cleaned/unique_edgelist.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
```

```{r}
attify <- function(net, attr_df){
  V(net)$iso_o <- V(net)$name
  idx <- match(V(net)$name, attr_df$iso_o)
  V(net)$country <- attr_df$country[idx]
  V(net)$D_log_gdp_pc <- attr_df$D_log_gdp_pc[idx]
  V(net)$landlocked <- attr_df$landlocked[idx]
  V(net)$continent <- attr_df$continent[idx]
  V(net)$development <- attr_df$development[idx]
  V(net)$langoff_1 <- attr_df$langoff_1[idx]
  return(net)
}
```

```{r}
network_construction <- function(year, u, att_path = "../data/cleaned") {
  y_col <- paste0("X", year)
  edges <- u[, c("iso_o", "iso_d", y_col)]
  edges <- subset(edges, edges[[y_col]] > 0)
  edges <- edges[, c("iso_o", "iso_d")]
  att <- read.csv(paste0(att_path, "/attribute", year, ".csv"),header = TRUE,as.is = TRUE,stringsAsFactors = FALSE)
  att <- att[!duplicated(att$iso_o), ]
  net <- graph_from_data_frame(d = edges,directed = TRUE,vertices = data.frame(name = att$iso_o))
  net <- attify(net, att)
  return(net)
}

nets <- lapply(1995:2023, network_construction, u = u)
names(nets) <- 1995:2023

# Converting into network object. 'nets' is the igraph object and 'nets_network' is the network object
nets_network <- lapply(nets, intergraph::asNetwork)
```

```{r}
nets_network[["1995"]]
```

```{r}
detach(package:igraph)
require(tergm)
require(sna)
```

```{r}
list.vertex.attributes(nets_network[["1995"]])
```

```{r}
library(networkDynamic)
```

# RTA -> NetworkDynamic object
```{r}
#rta <- read.csv("../data/cleaned/rta_edgelist.csv", stringsAsFactors = FALSE)
#countries <- sort(unique(c(rta$iso_o, c(rta$iso_d))))
#years <- 1995:2023
#rta_matrix <- lapply(years, function(y) {m <- reshape2::acast(rta, iso_o ~ iso_d, value.var = paste0("X", y),fill = 0)
  # enforce identical node ordering
#  m <- m[countries, countries]
#  return(m)
#})

#names(rta_matrix) <- years

#nrta <- lapply(rta_matrix, function(m) {network::as.network(m, directed = TRUE, matrix.type = "adjacency")})
```

```{r}
#nrta[["1995"]]
```

```{r}
#class(nrta[[1]])
#names(nrta) # The order is chronological and fine. 
```


8 May, 2026, starts 12:44PM, ends 1:50PM
# The following code runs for 3 minutes 
```{r}
#net_dynamic_rta <- networkDynamic(network.list = nrta, start = 1995, end = 2023)
```

```{r}
#saveRDS(net_dynamic_rta, file = "../results/net_dynamic_rta.rds")

net_dynamic_rta <- readRDS("../results/net_dynamic_rta.rds")
```


```{r}
class(net_dynamic_rta)
```


```{r}
#install.packages("Rglpk")
```


```{r}
# dim(rta0)
# dim(colony)
# network.size(nrta0)
# network.size(net_un00)
# network.size(dist_net)
# network.size(colony)
```



# Estimating STERGM
Started: 12 May 2026 at 2:00PM, 12:13AM
Ended: 12 May, 2026 at 11AM (approximately)

```{r}
#Reference: https://www.rdocumentation.org/packages/ergm/versions/4.8.1/topics/edgecov-ergmTerm
set.seed(312)
unique_stgm <- tergm(nets_network ~ Form(~ edges + nodecov("D_log_gdp_pc") 
                                         + absdiff("D_log_gdp_pc") 
                                         + nodemix("development")
                                         + edgecov(net_dynamic_rta)
                                         + nodematch("landlocked")
                                         + edgecov(dist_net, "log_dist")
                                         + edgecov(contig_mat)
                                         + edgecov(colony)
                                         + edgecov(col_mat)
                                         + edgecov(lang_mat)
                                         + mutual) +
              Persist(~ edges + nodecov("D_log_gdp_pc")
                                         + absdiff("D_log_gdp_pc")
                                         + nodemix("development")
                                         + edgecov(net_dynamic_rta)
                                         + nodematch("landlocked")
                                         + edgecov(dist_net, "log_dist")
                                         + edgecov(contig_mat)
                                         + edgecov(colony)
                                         + edgecov(col_mat)
                                         + edgecov(lang_mat)
                                         + mutual), estimate = "CMLE", times = 1:30)
```

```{r}
saveRDS(unique_stgm, "../results/unique_stgm.rds")
#unique_stgm <- readRDS("../results/unique_stgm.rds")
```

```{r}
print(summary(unique_stgm))
```


```{r}
#dim(dist_net)
```


```{r}
pvals_u <- summary(unique_stgm)$coefficients[, "Pr(>|z|)"]
or_u <- exp(coef(unique_stgm))
ste <- sqrt(diag(unique_stgm$covar))
lci <- exp(coef(unique_stgm) - 1.96 * ste) # the lower bound of the 95% confidence interval (see https://en.wikipedia.org/wiki/1.96)
uci <- exp(coef(unique_stgm) + 1.96 * ste) 
oddsratios <- cbind(coef(unique_stgm), round(lci, digits = 4), round(or_u, digits = 4), round(uci, digits = 4), pvals_u)
dataframe_u1 =as.data.frame(oddsratios)
dataframe_u1$model_terms <- rownames(dataframe_u1)
rownames(dataframe_u1) <- NULL
colnames(dataframe_u1) <- c('Estimate_u','lCI_u', 'OR_u','uCI_u', 'pvals_u', 'model_terms')
```


```{r}
#knitr::kable(coef(summary(unique_stgm)))
```

```{r}
dataframe_u1
```

```{r}
write.csv(dataframe_u1, "../results/unique_stgm1_results.csv")
```



```{r}
AIC(unique_stgm)[1]
BIC(unique_stgm)[1]
```

Start: 1:29AM
```{r}
goftest_u <- gof(unique_stgm) 
```

```{r}
saveRDS(goftest_u, "../results/goftest_model1_u.rds")
plot(goftest_u)
```


```{r}
#goftest_u <- readRDS("../results/goftest_model1_u.rds")
#names(goftest)
```

```{r}
#Reference: https://www.datamentor.io/r-programming/saving-plot#:~:text=Save%20as%20tiff%20Image,filename%20%3D%20%22saving_plot3%22)%20.
all_stats <- c("odegree", "idegree", "espartners", "distance", "model")
selected_stats <- all_stats[2:5]
tiff(file = "../results/goftest_model1_u.tiff",width = 12, height = 3, units = "in", res = 100)
par(mfrow = c(1, 4),mar = c(5, 5, 5, 1),oma = c(0.2, 1, 0.2, 1))
for (stat in selected_stats) {
  plot(goftest_u, which = stat, main = "Model 1", cex.lab = 1.5)}
dev.off()
```



