---
title: "STERGM on reproducible cultural goods trade"
author: "Author"
date: "2025-06-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

** Before excecuting this file I will clear all objects from the workspace and unload all packages from the currect environment with the following codes.**`



# Steps of STERGM:
1. Loading `network`, `igraph`, `intergraph` and `reshape2` packages
2. Making the distance network as a network object with edge weights as distances
3. Making four adjacency matrices with binary values for common colonizer, colonizer, common language, and contiguity
4. Defining a function to add node attributes to the networks
5. Loading the edgelist of unique cultural goods trade, and making 29 network objects for 29 consecutive years following the steps,     
    + Keeping only the pairs with positive weights
    + Subsetting the dataframe with only 'iso_o' and 'iso_d' column
    + Making an igraph object and assigning node attributes from the function created in the third step
    + Making a function for repeating the above four steps for all the years.
6. Converting all 24 igraph objects to network objects
7. Checking the node attributes for all of the networks
8. Making RTA adjacency matrices for all 29 years and converting it to a networkDynamic object. 
10. Running STERGM, calculating odds ratios, standard errors, and confidence intervals, and plotting goodness of fit and MCMC statistics
```{r}
#Reference: https://www.r-bloggers.com/2024/03/unload-all-packages-in-r-best-practices/
#install.packages("pacman")
#pacman::p_unload(pacman::p_loaded(), character.only = TRUE) 
```

```{r}
library(network)
library(igraph)
library(intergraph)
library(reshape2)
```

```{r}
lang <- read.csv("../data/cleaned/language_edgelist.csv",stringsAsFactors = FALSE)
lang_mat <- acast(lang, iso_o ~ iso_d, value.var = "comlang_off", fill = 0)

contiguity <- read.csv("../data/cleaned/contiguity_edgelist.csv",stringsAsFactors = FALSE)
contig_mat <- acast(contiguity, iso_o ~ iso_d, value.var = "contig", fill = 0)

common_col <- read.csv("../data/cleaned/comcol_edgelist.csv",stringsAsFactors = FALSE)
col_mat <- acast(common_col, iso_o ~ iso_d, value.var = "comcol", fill = 0)

colonizer <- read.csv("../data/cleaned/colonizer_edgelist.csv",stringsAsFactors = FALSE)
colony <- acast(colonizer, iso_o ~ iso_d, value.var = "colony", fill = 0)

dist_1 <- read.csv("../data/cleaned/distance_edgelist.csv",stringsAsFactors = FALSE)
dist_net <- network(dist_1[, c("iso_o", "iso_d")], 
                   directed = TRUE, 
                   matrix.type = "edgelist", 
                   loops = FALSE)

set.edge.value(dist_net, "log_dist", dist_1$log_dist)
```

```{r}
class(dist_net)
```

# Reproducible-culture Goods trade edgelist
```{r}
r <- read.csv("../data/cleaned/reproducible_edgelist.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
```

```{r}
attify <- function(net, attr_df){
  V(net)$iso_o <- V(net)$name
  idx <- match(V(net)$name, attr_df$iso_o)
  V(net)$country <- attr_df$country[idx]
  V(net)$D_log_gdp_pc <- attr_df$D_log_gdp_pc[idx]
  V(net)$landlocked <- attr_df$landlocked[idx]
  V(net)$continent <- attr_df$continent[idx]
  V(net)$development <- attr_df$development[idx]
  V(net)$langoff_1 <- attr_df$langoff_1[idx]
  return(net)
}
```

```{r}
network_construction <- function(year, r, att_path = "../data/cleaned") {
  y_col <- paste0("X", year)
  edges <- r[, c("iso_o", "iso_d", y_col)]
  edges <- subset(edges, edges[[y_col]] > 0)
  edges <- edges[, c("iso_o", "iso_d")]
  att <- read.csv(paste0(att_path, "/attribute", year, ".csv"),header = TRUE,as.is = TRUE,stringsAsFactors = FALSE)
  att <- att[!duplicated(att$iso_o), ]
  net <- graph_from_data_frame(d = edges,directed = TRUE,vertices = data.frame(name = att$iso_o))
  net <- attify(net, att)
  return(net)
}

nets <- lapply(1995:2023, network_construction, r = r)
names(nets) <- 1995:2023

# Converting into network object. 'nets' is the igraph object and 'nets_network' is the network object
nets_network_r <- lapply(nets, intergraph::asNetwork)
```

```{r}
nets_network_r[["1995"]]
```

```{r}
#list.vertex.attributes(nets_network_r[["1995"]])
```


```{r}
#library(sna)
#library(network)
library(networkDynamic)
```


```{r}
net_dynamic_rta <- readRDS("../results/net_dynamic_rta.rds")
```

```{r}
detach(package:igraph)
require(tergm)
require(sna)
```


# Estimating STERGM
Start: 11 May, 2026 at 03:28AM
End: 11 May, 2026 at 05:35PM
```{r}
#Reference: https://www.rdocumentation.org/packages/ergm/versions/4.8.1/topics/edgecov-ergmTerm

set.seed(312)
repro_stgm <- tergm(nets_network_r ~ Form(~ edges + nodecov("D_log_gdp_pc") 
                                         + absdiff("D_log_gdp_pc") 
                                         + nodemix("development")
                                         + edgecov(net_dynamic_rta)
                                         + nodematch("landlocked")
                                         + edgecov(dist_net, "log_dist")
                                         + edgecov(contig_mat)
                                         + edgecov(colony)
                                         + edgecov(col_mat)
                                         + edgecov(lang_mat)
                                         + mutual) +
              Persist(~ edges + nodecov("D_log_gdp_pc")
                                         + absdiff("D_log_gdp_pc")
                                         + nodemix("development")
                                         + edgecov(net_dynamic_rta)
                                         + nodematch("landlocked")
                                         + edgecov(dist_net, "log_dist")
                                         + edgecov(contig_mat)
                                         + edgecov(colony)
                                         + edgecov(col_mat)
                                         + edgecov(lang_mat)
                                         + mutual), estimate = "CMLE", times = 1:30)
```


```{r}
#saveRDS(repro_stgm, "../results/reproducible_stgm.rds")

repro_stgm <- readRDS("../results/reproducible_stgm.rds")
```


```{r}
print(summary(repro_stgm))
```

```{r}
or_r <- exp(coef(repro_stgm))
pvals_r <- summary(repro_stgm)$coefficients[, "Pr(>|z|)"]
ste1 <- sqrt(diag(repro_stgm$covar))
lci1 <- exp(coef(repro_stgm) - 1.96 * ste1) # the lower bound of the 95% confidence interval (see https://en.wikipedia.org/wiki/1.96)
uci1 <- exp(coef(repro_stgm) + 1.96 * ste1) # the upper bound of the 95% confidence interval (see https://en.wikipedia.org/wiki/1.96)

oddsratios1 <- cbind(coef(repro_stgm), round(lci1, digits = 4), round(or_r, digits = 4), round(uci1, digits = 4), pvals_r)
dataframe_r1 = as.data.frame(oddsratios1)
dataframe_r1$model_terms <- rownames(dataframe_r1)
rownames(dataframe_r1) <- NULL
colnames(dataframe_r1) <- c('est_r','lci_r', 'odds_r','uci_r', 'pvals_r', 'model_terms')
```

```{r}
write.csv(dataframe_r1, "../results/reproducible_stgm2_results.csv")
```

```{r}
dataframe_r1
```



## Goodness of fit statistics

```{r}
AIC(repro_stgm)[1]
BIC(repro_stgm)[1]
```
# start: 5:35PM, EndL: 11:56PM
```{r}
#goftest_repro <- gof(repro_stgm)
#plot(goftest_r)
#saveRDS(goftest_repro, "../results/goftest_model2_r.rds")
goftest_repro <- readRDS("../results/goftest_model2_r.rds")
```

```{r}
all_stats_3 <- c("odegree", "idegree", "espartners", "distance", "model")
# 2 to 5
selected_stats_3 <- all_stats_3[2:5]
tiff(file = "../results/goftest_model2_r.tiff",width = 12, height = 3, units = "in", res = 100)

par(mfrow = c(1, 4),mar = c(5, 5, 5, 1),oma = c(0.2, 1, 0.2, 1))
for (stat in selected_stats_3) {plot(goftest_repro, which = stat, main = "Model 2",cex.lab = 1.5)}
dev.off()
```

