---
title: "Measuring centralities of unique cultural goods trade networks"
author: "Author"
date: "2025-05-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(igraph)
```

## Steps: 
1. Reading the edgelist for unique cultural goods trade
2. Making 24 subsets of the edgelist with 24 different year columns
3. Doing the followings for each subset:
   a. Making igraph object from each one of them
   b. Reading each attribute file while merging the 'iso_o' values as vertex names with the igraph object
   c. making sure the igraph object used the vertex attributes
   d. Setting the edge weight
   e. Sanity checking for 
    * The graph is directed
    * Edge weights are valid-
    * Vertex names are unique and character
    * No self-loops or duplicate vertices
    * You’ve added only vertex attributes
4. Counting the number of nodes of all 24 networks to see if all matches
5. converting all 24 networks to 'wdnet' object
6. Finding out global and average local clustering coefficients
7. Finding out assortativity coefficient of four types
8. Making data frame with rows as times and the measures computed in step 6 and 7, saving that in the 'cleaned' subfolder of thedata' folder
9. Measuring  centralities of each network and making a dataframe for the respective years network metrices and saving that as a csv file in the 'cleaned' subfolder of th 'data' folder

10. Making a time series data for the global metrices of the network and saving a csv file in the 'cleaned' subfolder of th 'data' folder

```{r}
u <- read.csv("../data/cleaned/unique_edgelist.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
```

## 2000
```{r}
y0 <- "X2000"
u_y0 <- u[, c("iso_o", "iso_d", y0)]
u_y0 <- subset(u_y0, u_y0[[y0]] > 0)
att2000 <- read.csv("../data/cleaned/attribute2000.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un00 <- graph_from_data_frame(d = u_y0, directed = TRUE)
E(un00)$weight <- u_y0[[y0]]
is_directed(un00) 
length(E(un00)) == length(E(un00)$weight)
length(unique(V(un00)$name)) == gorder(un00)  
is.character(V(un00)$name) 
any(is.na(E(un00)$weight))     
any(!is.finite(E(un00)$weight))
edge_list <- as_data_frame(un00, what = "edges")
duplicated_rows <- duplicated(edge_list[, c("from", "to")])
any(duplicated_rows) 
length(unique(V(un00)$name))
```

```{r}
attify <- function(n_net, attr_df){
  V(n_net)$iso_o <- V(n_net)$name
  idx <- match(V(n_net)$name, attr_df$iso_o)
  V(n_net)$country <- attr_df$Country[idx]
  V(n_net)$D_log_gdp <- attr_df$D_log_gdp[idx]
  V(n_net)$D_log_gdp_pct <- attr_df$D_log_gdp_pct[idx]
  V(n_net)$log_population <- attr_df$log_population[idx]
  V(n_net)$log_trade_gdp_ratio <- attr_df$log_trade_gdp_ratio[idx]
  V(n_net)$landlocked <- attr_df$landlocked[idx]
  V(n_net)$continent <- attr_df$continent[idx]
  V(n_net)$lat <- attr_df$lat[idx]
  V(n_net)$lon <- attr_df$lon[idx]
  V(n_net)$development <- attr_df$development[idx]
  
  return(n_net)
}

un00 <- attify(un00, att2000)
vertex_attr_names(un00)
```


```{r}
summary(E(un00)$weight)
hist(E(un00)$weight, breaks = 100)
```
```{r}
class(un00)
```




```{r}
library(wdnet)
g1 <- igraph_to_wdnet(un00)
class(g1)
summary(g1)
print(g1, node.attrs = TRUE, edge.attrs = TRUE)
```


```{r}
node_names1 <- g1$node.attr$iso_o  

pageRank0 <- centrality(g1, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness0 <- centrality(g1, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree0 <- centrality(g1, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree0 <- centrality(g1, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct01 <- clustcoef(g1, method = "Clemente")$total$localcc
lct02 <- clustcoef(g1, method = "Clemente")$out$localcc

centrality_df0 <- data.frame(iso_o = node_names1, pageRank_unique = pageRank0, close_unique = closeness0, outdegree_unique = outdegree0, indegree_unique = indegree0, local_clust_tt_unique = lct01, local_clust_out_unique = lct02)
head(centrality_df0)
```


```{r}
write.csv(centrality_df0, "../data/cleaned/network_metrics_unique2000.csv")
```

# 2001
```{r}
y1 <- "X2001"   
u_y1 <- u[, c("iso_o", "iso_d", y1)]
u_y1 <- subset(u_y1, u_y1[[y1]] > 0)
att2001 <- read.csv("../data/cleaned/attribute2001.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un01 <- graph_from_data_frame(d = u_y1, directed = TRUE)
E(un01)$weight <- u_y1[[y1]]
is_directed(un01) 
length(E(un01)) == length(E(un01)$weight)
length(unique(V(un01)$name)) == gorder(un01)  
is.character(V(un01)$name) 
any(is.na(E(un01)$weight))      
any(!is.finite(E(un01)$weight)) 
edge_list1 <- as_data_frame(un01, what = "edges")
duplicated_rows1 <- duplicated(edge_list1[, c("from", "to")])
any(duplicated_rows1)  
length(unique(V(un01)$name))
un01 <- attify(un01, att2001)
vertex_attr_names(un01)
```

```{r}
class(un01)
g2 <- igraph_to_wdnet(un01)
class(g2)
summary(g2)
print(g2, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names2 <- g2$node.attr$iso_o 

pageRank1 <- centrality(g2, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness1 <- centrality(g2, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree1 <- centrality(g2, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree1 <- centrality(g2, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct11 <- clustcoef(g2, method = "Clemente")$total$localcc
lct12 <- clustcoef(g2, method = "Clemente")$out$localcc

centrality_df1 <- data.frame(iso_o = node_names2, pageRank_unique = pageRank1, close_unique = closeness1, outdegree_unique = outdegree1, indegree_unique = indegree1, local_clust_tt_unique = lct11, local_clust_out_unique = lct12)
centrality_df1
write.csv(centrality_df1, "../data/cleaned/network_metrics_unique2001.csv")
```


## 2002
```{r}
y2 <- "X2002"   
u_y2 <- u[, c("iso_o", "iso_d", y2)]
u_y2 <- subset(u_y2, u_y2[[y2]] > 0)
att2002 <- read.csv("../data/cleaned/attribute2002.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un02 <- graph_from_data_frame(d = u_y2, directed = TRUE)
E(un02)$weight <- u_y2[[y2]]
is_directed(un02) 
length(E(un02)) == length(E(un02)$weight)
length(unique(V(un02)$name)) == gorder(un02)  
is.character(V(un02)$name) 
any(is.na(E(un02)$weight))      
any(!is.finite(E(un02)$weight))
edge_list2 <- as_data_frame(un02, what = "edges")
duplicated_rows2 <- duplicated(edge_list2[, c("from", "to")])
any(duplicated_rows2)  
length(unique(V(un02)$name))
un02 <- attify(un02, att2002)
vertex_attr_names(un02)

```
```{r}
class(un02)
g3 <- igraph_to_wdnet(un02)
class(g3)
summary(g3)
print(g3, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names3 <- g3$node.attr$iso_o  

pageRank2 <- centrality(g3, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness2 <- centrality(g3, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree2 <- centrality(g3, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree2 <- centrality(g3, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct21 <- clustcoef(g3, method = "Clemente")$total$localcc
lct22 <- clustcoef(g3, method = "Clemente")$out$localcc

centrality_df2 <- data.frame(iso_o = node_names3, pageRank_unique = pageRank2, close_unique = closeness2, outdegree_unique = outdegree2, indegree_unique = indegree2, local_clust_tt_unique = lct21, local_clust_out_unique = lct22)
centrality_df2
write.csv(centrality_df2, "../data/cleaned/network_metrics_unique2002.csv")
```


## 2003
```{r}
y3 <- "X2003"   
u_y3 <- u[, c("iso_o", "iso_d", y3)]
u_y3 <- subset(u_y3, u_y3[[y3]] > 0)
att2003 <- read.csv("../data/cleaned/attribute2003.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un03 <- graph_from_data_frame(d = u_y3, directed = TRUE)
E(un03)$weight <- u_y3[[y3]]
is_directed(un03) 
length(E(un03)) == length(E(un03)$weight)
length(unique(V(un03)$name)) == gorder(un03)  
is.character(V(un03)$name) 
any(is.na(E(un03)$weight))      
any(!is.finite(E(un03)$weight))
edge_list3 <- as_data_frame(un03, what = "edges")
duplicated_rows3 <- duplicated(edge_list3[, c("from", "to")])
any(duplicated_rows3) 
length(unique(V(un03)$name))
un03 <- attify(un03, att2003)
vertex_attr_names(un03)
```
```{r}
class(un03)
g4 <- igraph_to_wdnet(un03)
class(g4)
summary(g4)
print(g4, node.attrs = TRUE, edge.attrs = TRUE)
```
```{r}
node_names4 <- g4$node.attr$iso_o  

pageRank3 <- centrality(g4, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness3 <- centrality(g4, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree3 <- centrality(g4, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree3 <- centrality(g4, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct31 <- clustcoef(g4, method = "Clemente")$total$localcc
lct32 <- clustcoef(g4, method = "Clemente")$out$localcc

centrality_df3 <- data.frame(iso_o = node_names4, pageRank_unique = pageRank3, close_unique = closeness3, outdegree_unique = outdegree3, indegree_unique = indegree3, local_clust_tt_unique = lct31, local_clust_out_unique = lct32)
centrality_df3
write.csv(centrality_df3, "../data/cleaned/network_metrics_unique2003.csv")
```

# 2004
```{r}
y4 <- "X2004"   
u_y4 <- u[, c("iso_o", "iso_d", y4)]
u_y4 <- subset(u_y4, u_y4[[y4]] > 0)
att2004 <- read.csv("../data/cleaned/attribute2004.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un04 <- graph_from_data_frame(d = u_y4, directed = TRUE)
E(un04)$weight <- u_y4[[y4]]
is_directed(un04) 
length(E(un04)) == length(E(un04)$weight)
length(unique(V(un04)$name)) == gorder(un04) 
is.character(V(un04)$name) 
any(is.na(E(un04)$weight))      
any(!is.finite(E(un04)$weight)) 
edge_list4 <- as_data_frame(un04, what = "edges")
duplicated_rows4 <- duplicated(edge_list4[, c("from", "to")])
any(duplicated_rows4)  
length(unique(V(un04)$name))
un04 <- attify(un04, att2004)
vertex_attr_names(un04)
```

```{r}
class(un04)
g5 <- igraph_to_wdnet(un04)
class(g5)
summary(g5)
print(g5, node.attrs = TRUE, edge.attrs = TRUE)

```
```{r}
node_names5 <- g5$node.attr$iso_o  

pageRank4 <- centrality(g5, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness4 <- centrality(g5, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree4 <- centrality(g5, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree4 <- centrality(g5, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct41 <- clustcoef(g5, method = "Clemente")$total$localcc
lct42 <- clustcoef(g5, method = "Clemente")$out$localcc


centrality_df4 <- data.frame(iso_o = node_names5, pageRank_unique = pageRank4, close_unique = closeness4, outdegree_unique = outdegree4, indegree_unique = indegree4, local_clust_tt_unique = lct41, local_clust_out_unique = lct42)
centrality_df4
write.csv(centrality_df4, "../data/cleaned/network_metrics_unique2004.csv")

```


# 2005
```{r}
y5 <- "X2005"   
u_y5 <- u[, c("iso_o", "iso_d", y5)]
u_y5 <- subset(u_y5, u_y5[[y5]] > 0)
att2005 <- read.csv("../data/cleaned/attribute2005.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un05 <- graph_from_data_frame(d = u_y5, directed = TRUE)
E(un05)$weight <- u_y5[[y5]]
is_directed(un05) 
length(E(un05)) == length(E(un05)$weight)
length(unique(V(un05)$name)) == gorder(un05)  
is.character(V(un05)$name) 
any(is.na(E(un05)$weight))      
any(!is.finite(E(un05)$weight)) 
edge_list5 <- as_data_frame(un05, what = "edges")
duplicated_rows5 <- duplicated(edge_list5[, c("from", "to")])
any(duplicated_rows5) 
length(unique(V(un05)$name))
un05 <- attify(un05, att2005)
vertex_attr_names(un05)
```

```{r}
class(un05)
g6 <- igraph_to_wdnet(un05)
class(g6)
summary(g6)
print(g6, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names6 <- g6$node.attr$iso_o  

pageRank5 <- centrality(g6, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness5 <- centrality(g6, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree5 <- centrality(g6, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree5 <- centrality(g6, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct51 <- clustcoef(g6, method = "Clemente")$total$localcc
lct52 <- clustcoef(g6, method = "Clemente")$out$localcc

centrality_df5 <- data.frame(iso_o = node_names6, pageRank_unique = pageRank5, close_unique = closeness5, outdegree_unique = outdegree5, indegree_unique = indegree5, local_clust_tt_unique = lct51, local_clust_out_unique = lct52)
centrality_df5
write.csv(centrality_df5, "../data/cleaned/network_metrics_unique2005.csv")
```

# 2006
```{r}
y6 <- "X2006"   
u_y6 <- u[, c("iso_o", "iso_d", y6)]
u_y6 <- subset(u_y6, u_y6[[y6]] > 0)
att2006 <- read.csv("../data/cleaned/attribute2006.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un06 <- graph_from_data_frame(d = u_y6, directed = TRUE)
E(un06)$weight <- u_y6[[y6]]
is_directed(un06) 
length(E(un06)) == length(E(un06)$weight)
length(unique(V(un06)$name)) == gorder(un06) 
is.character(V(un06)$name) 
any(is.na(E(un06)$weight))      
any(!is.finite(E(un06)$weight)) 
edge_list6 <- as_data_frame(un06, what = "edges")
duplicated_rows6 <- duplicated(edge_list6[, c("from", "to")])
any(duplicated_rows6) 
length(unique(V(un06)$name))
un06 <- attify(un06, att2006)
vertex_attr_names(un06)

```

```{r}
class(un06)
g7 <- igraph_to_wdnet(un06)
class(g7)
summary(g7)
print(g7, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names7 <- g7$node.attr$iso_o  
pageRank6 <- centrality(g7, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness6 <- centrality(g7, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree6 <- centrality(g7, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree6 <- centrality(g7, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct61 <- clustcoef(g7, method = "Clemente")$total$localcc
lct62 <- clustcoef(g7, method = "Clemente")$out$localcc

centrality_df6 <- data.frame(iso_o = node_names7, pageRank_unique = pageRank6, close_unique = closeness6, outdegree_unique = outdegree6, indegree_unique = indegree6,local_clust_tt_unique = lct61, local_clust_out_unique = lct62)
centrality_df6
write.csv(centrality_df6, "../data/cleaned/network_metrics_unique2006.csv")

```

## 2007
```{r}
y7 <- "X2007"   
u_y7 <- u[, c("iso_o", "iso_d", y7)]
u_y7 <- subset(u_y7, u_y7[[y7]] > 0)
att2007 <- read.csv("../data/cleaned/attribute2007.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un07 <- graph_from_data_frame(d = u_y7, directed = TRUE)
E(un07)$weight <- u_y7[[y7]]
is_directed(un07) 
length(E(un07)) == length(E(un07)$weight)
length(unique(V(un07)$name)) == gorder(un07)  
is.character(V(un07)$name) 
any(is.na(E(un07)$weight))      
any(!is.finite(E(un07)$weight)) 
edge_list7 <- as_data_frame(un07, what = "edges")
duplicated_rows7 <- duplicated(edge_list7[, c("from", "to")])
any(duplicated_rows7)  
length(unique(V(un07)$name))
un07 <- attify(un07, att2007)
vertex_attr_names(un07)
```
```{r}
class(un07)
g8 <- igraph_to_wdnet(un07)
class(g8)
summary(g8)
print(g8, node.attrs = TRUE, edge.attrs = TRUE)

```

```{r}
node_names8 <- g8$node.attr$iso_o 
pageRank7 <- centrality(g8, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness7 <- centrality(g8, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree7 <- centrality(g8, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree7 <- centrality(g8, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct71 <- clustcoef(g8, method = "Clemente")$total$localcc
lct72 <- clustcoef(g8, method = "Clemente")$out$localcc
```

```{r}
centrality_df7 <- data.frame(iso_o = node_names8, pageRank_unique = pageRank7, close_unique = closeness7, outdegree_unique = outdegree7, indegree_unique = indegree7, local_clust_tt_unique = lct71, local_clust_out_unique = lct72)
centrality_df7
write.csv(centrality_df7, "../data/cleaned/network_metrics_unique2007.csv")

```


## 2008
```{r}
y8 <- "X2008"   
u_y8 <- u[, c("iso_o", "iso_d", y8)]
u_y8 <- subset(u_y8, u_y8[[y8]] > 0)
att2008 <- read.csv("../data/cleaned/attribute2008.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un08 <- graph_from_data_frame(d = u_y8, directed = TRUE)
E(un08)$weight <- u_y8[[y8]]
is_directed(un08) 
length(E(un08)) == length(E(un08)$weight)
length(unique(V(un08)$name)) == gorder(un08)  
is.character(V(un08)$name) 
any(is.na(E(un08)$weight))      
any(!is.finite(E(un08)$weight)) 
edge_list8 <- as_data_frame(un08, what = "edges")
duplicated_rows8 <- duplicated(edge_list8[, c("from", "to")])
any(duplicated_rows8)  
length(unique(V(un08)$name))
un08 <- attify(un08, att2008)
vertex_attr_names(un08)

```

```{r}
class(un08)
g9 <- igraph_to_wdnet(un08)
class(g9)
summary(g9)
print(g9, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names9 <- g9$node.attr$iso_o 
pageRank8 <- centrality(g9, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness8 <- centrality(g9, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree8 <- centrality(g9, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree8 <- centrality(g9, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct81 <- clustcoef(g9, method = "Clemente")$total$localcc
lct82 <- clustcoef(g9, method = "Clemente")$out$localcc

```

```{r}
centrality_df8 <- data.frame(iso_o = node_names9, pageRank_unique = pageRank8, close_unique = closeness8, outdegree_unique = outdegree8, indegree_unique = indegree8,local_clust_tt_unique = lct81, local_clust_out_unique = lct82)
centrality_df8
write.csv(centrality_df8, "../data/cleaned/network_metrics_unique2008.csv")
```


## 2009
```{r}
y9 <- "X2009"   
u_y9 <- u[, c("iso_o", "iso_d", y9)]
u_y9 <- subset(u_y9, u_y9[[y9]] > 0)
att2009 <- read.csv("../data/cleaned/attribute2009.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un09 <- graph_from_data_frame(d = u_y9, directed = TRUE)
E(un09)$weight <- u_y9[[y9]]
is_directed(un09) 
length(E(un09)) == length(E(un09)$weight)
length(unique(V(un09)$name)) == gorder(un09)  
is.character(V(un09)$name) 
any(is.na(E(un09)$weight))      
any(!is.finite(E(un09)$weight)) 
edge_list9 <- as_data_frame(un09, what = "edges")
duplicated_rows9 <- duplicated(edge_list9[, c("from", "to")])
any(duplicated_rows9) 
length(unique(V(un09)$name))
un09 <- attify(un09, att2009)
vertex_attr_names(un09)

```

```{r}
class(un09)
g10 <- igraph_to_wdnet(un09)
class(g10)
summary(g10)
print(g10, node.attrs = TRUE, edge.attrs = TRUE)

```

```{r}
node_names10 <- g10$node.attr$iso_o 
pageRank9 <- centrality(g10, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness9 <- centrality(g10, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree9 <- centrality(g10, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree9 <- centrality(g10, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct91 <- clustcoef(g10, method = "Clemente")$total$localcc
lct92 <- clustcoef(g10, method = "Clemente")$out$localcc

```

```{r}
centrality_df9 <- data.frame(iso_o = node_names10, pageRank_unique = pageRank9, close_unique = closeness9, outdegree_unique = outdegree9, indegree_unique = indegree9, local_clust_tt_unique = lct91, local_clust_out_unique = lct92)
centrality_df9
write.csv(centrality_df9, "../data/cleaned/network_metrics_unique2009.csv")
```


## 2010
```{r}
y10 <- "X2010"   
u_y10 <- u[, c("iso_o", "iso_d", y10)]
u_y10 <- subset(u_y10, u_y10[[y10]] > 0)
att2010 <- read.csv("../data/cleaned/attribute2010.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un10 <- graph_from_data_frame(d = u_y10, directed = TRUE)
E(un10)$weight <- u_y10[[y10]]
is_directed(un10) 
length(E(un10)) == length(E(un10)$weight)
length(unique(V(un10)$name)) == gorder(un10)  
is.character(V(un10)$name) 
any(is.na(E(un10)$weight))      
any(!is.finite(E(un10)$weight)) 
edge_list10 <- as_data_frame(un10, what = "edges")
duplicated_rows10 <- duplicated(edge_list10[, c("from", "to")])
any(duplicated_rows10) 
length(unique(V(un10)$name))
un10 <- attify(un10, att2010)
vertex_attr_names(un10)

```
```{r}
class(un10)
g11 <- igraph_to_wdnet(un10)
class(g11)
summary(g11)
print(g11, node.attrs = TRUE, edge.attrs = TRUE)

```

```{r}
node_names11 <- g11$node.attr$iso_o 
pageRank10 <- centrality(g11, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness10 <- centrality(g11, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree10 <- centrality(g11, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree10 <- centrality(g11, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct101 <- clustcoef(g11, method = "Clemente")$total$localcc
lct102 <- clustcoef(g11, method = "Clemente")$out$localcc
```
```{r}
centrality_df10 <- data.frame(iso_o = node_names11, pageRank_unique = pageRank10, close_unique = closeness10, outdegree_unique = outdegree10, indegree_unique = indegree10, local_clust_tt_unique = lct101, local_clust_out_unique = lct102)
centrality_df10
write.csv(centrality_df10, "../data/cleaned/network_metrics_unique2010.csv")
```

## 2011
```{r}
y11 <- "X2011"   
u_y11 <- u[, c("iso_o", "iso_d", y11)]
u_y11 <- subset(u_y11, u_y11[[y11]] > 0)
att2011 <- read.csv("../data/cleaned/attribute2011.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un11 <- graph_from_data_frame(d = u_y11, directed = TRUE)
E(un11)$weight <- u_y11[[y11]]
is_directed(un11) 
length(E(un11)) == length(E(un11)$weight)
length(unique(V(un11)$name)) == gorder(un11)  
is.character(V(un11)$name) 
any(is.na(E(un11)$weight))      
any(!is.finite(E(un11)$weight)) 
edge_list11 <- as_data_frame(un11, what = "edges")
duplicated_rows11 <- duplicated(edge_list11[, c("from", "to")])
any(duplicated_rows11)  
length(unique(V(un11)$name))
un11 <- attify(un11, att2011)
vertex_attr_names(un11)
```

```{r}
class(un11)
g12 <- igraph_to_wdnet(un11)
class(g12)
summary(g12)
print(g12, node.attrs = TRUE, edge.attrs = TRUE)
```

```{r}
node_names12 <- g12$node.attr$iso_o 
pageRank11 <- centrality(g12, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness11 <- centrality(g12, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree11 <- centrality(g12, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree11 <- centrality(g12, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct111 <- clustcoef(g12, method = "Clemente")$total$localcc
lct112 <- clustcoef(g12, method = "Clemente")$out$localcc

```

```{r}
centrality_df11 <- data.frame(iso_o = node_names12, pageRank_unique = pageRank11, close_unique = closeness11, outdegree_unique = outdegree11, indegree_unique = indegree11,local_clust_tt_unique = lct111, local_clust_out_unique = lct112)
centrality_df11
write.csv(centrality_df11, "../data/cleaned/network_metrics_unique2011.csv")

```


## 2012
```{r}
y12 <- "X2012"   
u_y12 <- u[, c("iso_o", "iso_d", y12)]
u_y12 <- subset(u_y12, u_y12[[y12]] > 0)
att2012 <- read.csv("../data/cleaned/attribute2012.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un12 <- graph_from_data_frame(d = u_y12, directed = TRUE)
E(un12)$weight <- u_y12[[y12]]
is_directed(un12) 
length(E(un12)) == length(E(un12)$weight)
length(unique(V(un12)$name)) == gorder(un12)  
is.character(V(un12)$name) 
any(is.na(E(un12)$weight))      
any(!is.finite(E(un12)$weight)) 
edge_list12 <- as_data_frame(un12, what = "edges")
duplicated_rows12 <- duplicated(edge_list12[, c("from", "to")])
any(duplicated_rows12)  
length(unique(V(un12)$name))
un12 <- attify(un12, att2012)
vertex_attr_names(un12)

```

```{r}
class(un12)
g13 <- igraph_to_wdnet(un12)
class(g13)
summary(g13)
print(g13, node.attrs = TRUE, edge.attrs = TRUE)

```

```{r}
node_names13 <- g13$node.attr$iso_o 
pageRank12 <- centrality(g13, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness12 <- centrality(g13, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree12 <- centrality(g13, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree12 <- centrality(g13, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct121 <- clustcoef(g13, method = "Clemente")$total$localcc
lct122 <- clustcoef(g13, method = "Clemente")$out$localcc
```

```{r}
centrality_df12 <- data.frame(iso_o = node_names13, pageRank_unique = pageRank12, close_unique = closeness12, outdegree_unique = outdegree12, indegree_unique = indegree12,local_clust_tt_unique = lct121, local_clust_out_unique = lct122)
centrality_df12
write.csv(centrality_df12, "../data/cleaned/network_metrics_unique2012.csv")
```

## 2013
```{r}
y13 <- "X2013"   
u_y13 <- u[, c("iso_o", "iso_d", y13)]
u_y13 <- subset(u_y13, u_y13[y13] > 0)
att2013 <- read.csv("../data/cleaned/attribute2013.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un13 <- graph_from_data_frame(d = u_y13, directed = TRUE)
E(un13)$weight <- u_y13[[y13]]
is_directed(un13) 
length(E(un13)) == length(E(un13)$weight)
length(unique(V(un13)$name)) == gorder(un13) 
is.character(V(un13)$name) 
any(is.na(E(un13)$weight))      
any(!is.finite(E(un13)$weight)) 
edge_list13 <- as_data_frame(un13, what = "edges")
duplicated_rows13 <- duplicated(edge_list13[, c("from", "to")])
any(duplicated_rows13)  
length(unique(V(un13)$name))
un13 <- attify(un13, att2013)
vertex_attr_names(un13)
```

```{r}
class(un13)
g14 <- igraph_to_wdnet(un13)
class(g14)
summary(g14)
print(g14, node.attrs = TRUE, edge.attrs = TRUE)

```

```{r}
node_names14 <- g14$node.attr$iso_o 
pageRank13 <- centrality(g14, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness13 <- centrality(g14, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree13 <- centrality(g14, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree13 <- centrality(g14, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct131 <- clustcoef(g14, method = "Clemente")$total$localcc
lct132 <- clustcoef(g14, method = "Clemente")$out$localcc
```

```{r}
centrality_df13 <- data.frame(iso_o = node_names14, pageRank_unique = pageRank13, close_unique = closeness13, outdegree_unique = outdegree13, indegree_unique = indegree13,local_clust_tt_unique = lct131, local_clust_out_unique = lct132)
centrality_df13
write.csv(centrality_df13, "../data/cleaned/network_metrics_unique2013.csv")

```


## 2014
```{r}
y14 <- "X2014"   
u_y14 <- u[, c("iso_o", "iso_d", y14)]
u_y14 <- subset(u_y14, u_y14[y14] > 0)
att2014 <- read.csv("../data/cleaned/attribute2014.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un14 <- graph_from_data_frame(d = u_y14, directed = TRUE)
E(un14)$weight <- u_y14[[y14]]
is_directed(un14) 
length(E(un14)) == length(E(un14)$weight)
length(unique(V(un14)$name)) == gorder(un14)  
is.character(V(un14)$name) 
any(is.na(E(un14)$weight))      
any(!is.finite(E(un14)$weight)) 
edge_list14 <- as_data_frame(un14, what = "edges")
duplicated_rows14 <- duplicated(edge_list14[, c("from", "to")])
any(duplicated_rows14)  
length(unique(V(un14)$name))
un14 <- attify(un14, att2014)
vertex_attr_names(un14)
```

```{r}
class(un14)
g15 <- igraph_to_wdnet(un14)
class(g15)
summary(g15)
print(g15, node.attrs = TRUE, edge.attrs = TRUE)

```

```{r}
node_names15 <- g15$node.attr$iso_o 
pageRank14 <- centrality(g15, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness14 <- centrality(g15, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree14 <- centrality(g15, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree14 <- centrality(g15, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct141 <- clustcoef(g15, method = "Clemente")$total$localcc
lct142 <- clustcoef(g15, method = "Clemente")$out$localcc

```

```{r}
centrality_df14 <- data.frame(iso_o = node_names15, pageRank_unique = pageRank14, close_unique = closeness14, outdegree_unique = outdegree14, indegree_unique = indegree14, local_clust_tt_unique = lct141, local_clust_out_unique = lct142)
centrality_df14
write.csv(centrality_df14, "../data/cleaned/network_metrics_unique2014.csv")
```

## 2015
```{r}
y15 <- "X2015"   
u_y15 <- u[, c("iso_o", "iso_d", y15)]
u_y15 <- subset(u_y15, u_y15[y15] > 0)
att2015 <- read.csv("../data/cleaned/attribute2015.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un15 <- graph_from_data_frame(d = u_y15, directed = TRUE)
E(un15)$weight <- u_y15[[y15]]
is_directed(un15) 
length(E(un15)) == length(E(un15)$weight)
length(unique(V(un15)$name)) == gorder(un15)  
is.character(V(un15)$name) 
any(is.na(E(un15)$weight))      
any(!is.finite(E(un15)$weight)) 
edge_list15 <- as_data_frame(un15, what = "edges")
duplicated_rows15 <- duplicated(edge_list15[, c("from", "to")])
any(duplicated_rows15)  
length(unique(V(un15)$name))
un15 <- attify(un15, att2015)
vertex_attr_names(un15)

```

```{r}
class(un15)
g16 <- igraph_to_wdnet(un15)
class(g16)
summary(g16)
print(g16, node.attrs = TRUE, edge.attrs = TRUE)

```

```{r}
node_names16 <- g16$node.attr$iso_o 
pageRank15 <- centrality(g16, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness15 <- centrality(g16, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree15 <- centrality(g16, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree15 <- centrality(g16, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct151 <- clustcoef(g16, method = "Clemente")$total$localcc
lct152 <- clustcoef(g16, method = "Clemente")$out$localcc

```

```{r}
centrality_df15 <- data.frame(iso_o = node_names16, pageRank_unique = pageRank15, close_unique = closeness15, outdegree_unique = outdegree15, indegree_unique = indegree15, local_clust_tt_unique = lct151, local_clust_out_unique = lct152)
centrality_df15
write.csv(centrality_df15, "../data/cleaned/network_metrics_unique2015.csv")
```


# 2016
```{r}
y16 <- "X2016"   
u_y16 <- u[, c("iso_o", "iso_d", y16)]
u_y16 <- subset(u_y16, u_y16[y16] > 0)
att2016 <- read.csv("../data/cleaned/attribute2016.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un16 <- graph_from_data_frame(d = u_y16, directed = TRUE)
E(un16)$weight <- u_y16[[y16]]
is_directed(un16) 
length(E(un16)) == length(E(un16)$weight)
length(unique(V(un16)$name)) == gorder(un16)  
is.character(V(un16)$name) 
any(is.na(E(un16)$weight))      
any(!is.finite(E(un16)$weight)) 
edge_list16 <- as_data_frame(un16, what = "edges")
duplicated_rows16 <- duplicated(edge_list16[, c("from", "to")])
any(duplicated_rows16)  
length(unique(V(un16)$name))
un16 <- attify(un16, att2016)
vertex_attr_names(un16)

```

```{r}
class(un16)
g17 <- igraph_to_wdnet(un16)
class(g17)
summary(g17)
print(g17, node.attrs = TRUE, edge.attrs = TRUE)

```

```{r}
node_names17 <- g17$node.attr$iso_o 
pageRank16 <- centrality(g17, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness16 <- centrality(g17, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree16 <- centrality(g17, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree16 <- centrality(g17, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct161 <- clustcoef(g17, method = "Clemente")$total$localcc
lct162 <- clustcoef(g17, method = "Clemente")$out$localcc

```

```{r}
centrality_df16 <- data.frame(iso_o = node_names17, pageRank_unique = pageRank16, close_unique = closeness16, outdegree_unique = outdegree16, indegree_unique = indegree16, local_clust_tt_unique = lct161, local_clust_out_unique = lct162)
centrality_df16
write.csv(centrality_df16, "../data/cleaned/network_metrics_unique2016.csv")
```

## 2017
```{r}
y17 <- "X2017"   
u_y17 <- u[, c("iso_o", "iso_d", y17)]
u_y17 <- subset(u_y17, u_y17[y17] > 0)
att2017 <- read.csv("../data/cleaned/attribute2017.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un17 <- graph_from_data_frame(d = u_y17, directed = TRUE)
E(un17)$weight <- u_y17[[y17]]
is_directed(un17) 
length(E(un17)) == length(E(un17)$weight)
length(unique(V(un17)$name)) == gorder(un17) 
is.character(V(un17)$name) 
any(is.na(E(un17)$weight))      
any(!is.finite(E(un17)$weight)) 
edge_list17 <- as_data_frame(un17, what = "edges")
duplicated_rows17 <- duplicated(edge_list17[, c("from", "to")])
any(duplicated_rows17)  
length(unique(V(un17)$name))
un17 <- attify(un17, att2017)
vertex_attr_names(un17)

```

```{r}
class(un17)
g18 <- igraph_to_wdnet(un17)
class(g18)
summary(g18)
print(g18, node.attrs = TRUE, edge.attrs = TRUE)

```

```{r}
node_names18 <- g18$node.attr$iso_o 
pageRank17 <- centrality(g18, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness17 <- centrality(g18, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree17 <- centrality(g18, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree17 <- centrality(g18, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct171 <- clustcoef(g18, method = "Clemente")$total$localcc
lct172 <- clustcoef(g18, method = "Clemente")$out$localcc
```

```{r}
centrality_df17 <- data.frame(iso_o = node_names18, pageRank_unique = pageRank17, close_unique = closeness17, outdegree_unique = outdegree17, indegree_unique = indegree17, local_clust_tt_unique = lct171, local_clust_out_unique = lct172)
centrality_df17
write.csv(centrality_df17, "../data/cleaned/network_metrics_unique2017.csv")
```
## 2018
```{r}
y18 <- "X2018"   
u_y18 <- u[, c("iso_o", "iso_d", y18)]
u_y18 <- subset(u_y18, u_y18[y18] > 0)
att2018 <- read.csv("../data/cleaned/attribute2018.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un18 <- graph_from_data_frame(d = u_y18, directed = TRUE)
E(un18)$weight <- u_y18[[y18]]
is_directed(un18) 
length(E(un18)) == length(E(un18)$weight)
length(unique(V(un18)$name)) == gorder(un18)  
is.character(V(un18)$name) 
any(is.na(E(un18)$weight))      
any(!is.finite(E(un18)$weight)) 
edge_list18 <- as_data_frame(un18, what = "edges")
duplicated_rows18 <- duplicated(edge_list18[, c("from", "to")])
any(duplicated_rows18)  
length(unique(V(un18)$name))
un18 <- attify(un18, att2018)
vertex_attr_names(un18)
```
```{r}
class(un18)
g19<- igraph_to_wdnet(un18)
class(g19)
summary(g19)
vertex_attr_names(un18)
print(g19, node.attrs= TRUE, edge.attrs= TRUE)
```
```{r}
node_names19 <- g19$node.attr$iso_o 
pageRank18 <- centrality(g19, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness18 <- centrality(g19, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree18 <- centrality(g19, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree18 <- centrality(g19, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct181 <- clustcoef(g19, method = "Clemente")$total$localcc
lct182 <- clustcoef(g19, method = "Clemente")$out$localcc
```

```{r}
centrality_df18 <- data.frame(iso_o = node_names19, pageRank_unique = pageRank18, close_unique = closeness18, outdegree_unique = outdegree18, indegree_unique = indegree18, local_clust_tt_unique = lct181, local_clust_out_unique = lct182)
centrality_df18
write.csv(centrality_df18, "../data/cleaned/network_metrics_unique2018.csv")

```

## 2019
```{r}
y19 <- "X2019"   
u_y19 <- u[, c("iso_o", "iso_d", y19)]
u_y19 <- subset(u_y19, u_y19[y19] > 0)
att2019 <- read.csv("../data/cleaned/attribute2019.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un19 <- graph_from_data_frame(d = u_y19, directed = TRUE)
E(un19)$weight <- u_y19[[y19]]
is_directed(un19) 
length(E(un19)) == length(E(un19)$weight)
length(unique(V(un19)$name)) == gorder(un19)  
is.character(V(un19)$name) 
any(is.na(E(un19)$weight))      
any(!is.finite(E(un19)$weight)) 
edge_list19 <- as_data_frame(un19, what = "edges")
duplicated_rows19 <- duplicated(edge_list19[, c("from", "to")])
any(duplicated_rows19)  
length(unique(V(un19)$name))
un19 <- attify(un19, att2019)
vertex_attr_names(un19)

```

```{r}
class(un19)
g20<- igraph_to_wdnet(un19)
class(g20)
summary(g20)
vertex_attr_names(un19)
print(g20, node.attrs= TRUE, edge.attrs= TRUE)
```

```{r}
node_names20 <- g20$node.attr$iso_o 
pageRank19 <- centrality(g20, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness19 <- centrality(g20, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree19 <- centrality(g20, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree19 <- centrality(g20, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct191 <- clustcoef(g20, method = "Clemente")$total$localcc
lct192 <- clustcoef(g20, method = "Clemente")$out$localcc

centrality_df19 <- data.frame(iso_o = node_names20, pageRank_unique = pageRank19, close_unique = closeness19, outdegree_unique = outdegree19, indegree_unique = indegree19, local_clust_tt_unique = lct191, local_clust_out_unique = lct192)
centrality_df19
write.csv(centrality_df19, "../data/cleaned/network_metrics_unique2019.csv")
```


# 2020
```{r}
y20 <- "X2020"   
u_y20 <- u[, c("iso_o", "iso_d", y20)]
u_y20 <- subset(u_y20, u_y20[y20] > 0)
att2020 <- read.csv("../data/cleaned/attribute2020.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un20 <- graph_from_data_frame(d = u_y20, directed = TRUE)
E(un20)$weight <- u_y20[[y20]]
is_directed(un20) 
length(E(un20)) == length(E(un20)$weight)
length(unique(V(un20)$name)) == gorder(un20)  
is.character(V(un20)$name) 
any(is.na(E(un20)$weight))      
any(!is.finite(E(un20)$weight)) 
edge_list20 <- as_data_frame(un20, what = "edges")
duplicated_rows20 <- duplicated(edge_list20[, c("from", "to")])
any(duplicated_rows20)  
length(unique(V(un20)$name))
un20 <- attify(un20, att2020)
vertex_attr_names(un20)
```

```{r}
class(un20)
g21<- igraph_to_wdnet(un20)
class(g21)
summary(g21)
vertex_attr_names(un20)
print(g21, node.attrs= TRUE, edge.attrs= TRUE)

```

```{r}
node_names21 <- g21$node.attr$iso_o 
pageRank20 <- centrality(g21, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness20 <- centrality(g21, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree20 <- centrality(g21, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree20 <- centrality(g21, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct201 <- clustcoef(g21, method = "Clemente")$total$localcc
lct202 <- clustcoef(g21, method = "Clemente")$out$localcc

centrality_df20 <- data.frame(iso_o = node_names21, pageRank_unique = pageRank20, close_unique = closeness20, outdegree_unique = outdegree20, indegree_unique = indegree20, local_clust_tt_unique = lct201, local_clust_out_unique = lct202)
centrality_df20
write.csv(centrality_df20, "../data/cleaned/network_metrics_unique2020.csv")
```

# 2021
```{r}
y21 <- "X2021"   
u_y21 <- u[, c("iso_o", "iso_d", y21)]
u_y21 <- subset(u_y21, u_y21[y21] > 0)
att2021 <- read.csv("../data/cleaned/attribute2021.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un21 <- graph_from_data_frame(d = u_y21, directed = TRUE)
E(un21)$weight <- u_y21[[y21]]
is_directed(un21) 
length(E(un21)) == length(E(un21)$weight)
length(unique(V(un21)$name)) == gorder(un21)  
is.character(V(un21)$name) 
any(is.na(E(un21)$weight))      
any(!is.finite(E(un21)$weight)) 
edge_list21 <- as_data_frame(un21, what = "edges")
duplicated_rows21 <- duplicated(edge_list21[, c("from", "to")])
any(duplicated_rows21) 
length(unique(V(un21)$name))
un21 <- attify(un21, att2021)
vertex_attr_names(un21)

```

```{r}
class(un21)
g22 <- igraph_to_wdnet(un21)
class(g22)
summary(g22)
vertex_attr_names(un21)
print(g22, node.attrs= TRUE, edge.attrs= TRUE)
```

```{r}
node_names22 <- g22$node.attr$iso_o 
pageRank21 <- centrality(g22, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness21 <- centrality(g22, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree21 <- centrality(g22, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree21 <- centrality(g22, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct211 <- clustcoef(g22, method = "Clemente")$total$localcc
lct212 <- clustcoef(g22, method = "Clemente")$out$localcc

centrality_df21 <- data.frame(iso_o = node_names22, pageRank_unique = pageRank21, close_unique = closeness21, outdegree_unique = outdegree21, indegree_unique = indegree21,local_clust_tt_unique = lct211, local_clust_out_unique = lct212)
centrality_df21
write.csv(centrality_df21, "../data/cleaned/network_metrics_unique2021.csv")
```

# 2022
```{r}
y22 <- "X2022"   
u_y22 <- u[, c("iso_o", "iso_d", y22)]
u_y22 <- subset(u_y22, u_y22[y22] > 0)
att2022 <- read.csv("../data/cleaned/attribute2022.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un22 <- graph_from_data_frame(d = u_y22, directed = TRUE)
E(un22)$weight <- u_y22[[y22]]
is_directed(un22) 
length(E(un22)) == length(E(un22)$weight)
length(unique(V(un22)$name)) == gorder(un22) 
is.character(V(un22)$name) 
any(is.na(E(un22)$weight))      
any(!is.finite(E(un22)$weight)) 
edge_list22 <- as_data_frame(un22, what = "edges")
duplicated_rows22 <- duplicated(edge_list22[, c("from", "to")])
any(duplicated_rows22)  
length(unique(V(un22)$name))
un22 <- attify(un22, att2022)
vertex_attr_names(un22)

```

```{r}
class(un22)
g23 <- igraph_to_wdnet(un22)
class(g23)
summary(g23)
vertex_attr_names(un22)
print(g23, node.attrs= TRUE, edge.attrs= TRUE)

```

```{r}
node_names23 <- g23$node.attr$iso_o 
pageRank22 <- centrality(g23, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness22 <- centrality(g23, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree22 <- centrality(g23, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree22 <- centrality(g23, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct221 <- clustcoef(g23, method = "Clemente")$total$localcc
lct222 <- clustcoef(g23, method = "Clemente")$out$localcc

centrality_df22 <- data.frame(iso_o = node_names23, pageRank_unique = pageRank22, close_unique = closeness22, outdegree_unique = outdegree22, indegree_unique = indegree22, local_clust_tt_unique = lct221, local_clust_out_unique = lct222)
centrality_df22
write.csv(centrality_df22, "../data/cleaned/network_metrics_unique2022.csv")
```

#2023
```{r}
y23 <- "X2023"   
u_y23 <- u[, c("iso_o", "iso_d", y23)]
u_y23 <- subset(u_y23, u_y23[y23] > 0)
att2023 <- read.csv("../data/cleaned/attribute2023.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
un23 <- graph_from_data_frame(d = u_y23, directed = TRUE)
E(un23)$weight <- u_y23[[y23]]
is_directed(un23) 
length(E(un23)) == length(E(un23)$weight)
length(unique(V(un23)$name)) == gorder(un23)  
is.character(V(un23)$name) 
any(is.na(E(un23)$weight))      
any(!is.finite(E(un23)$weight)) 
edge_list23 <- as_data_frame(un23, what = "edges")
duplicated_rows23 <- duplicated(edge_list23[, c("from", "to")])
any(duplicated_rows23)  
length(unique(V(un23)$name))
un23 <- attify(un23, att2023)
vertex_attr_names(un23)

```

```{r}
class(un23)
g24 <- igraph_to_wdnet(un23)
class(g24)
summary(g24)
vertex_attr_names(un23)
print(g24, node.attrs= TRUE, edge.attrs= TRUE)
```

```{r}
node_names24 <- g24$node.attr$iso_o 
pageRank23 <- centrality(g24, measure = "wpr", wpr.control = list(gamma = 0.85, theta = 0.75))
closeness23 <- centrality(g24, measure = "closeness", closeness.control =list(alpha = 0.8, mode = "out", method = "harmonic", distance = FALSE))
outdegree23 <- centrality(g24, measure = "degree", degree.control = list(alpha = 0.8, mode = "out"))
indegree23 <- centrality(g24, measure = "degree", degree.control = list(alpha = 0.8, mode = "in"))
lct231 <- clustcoef(g24, method = "Clemente")$total$localcc
lct232 <- clustcoef(g24, method = "Clemente")$out$localcc

centrality_df23 <- data.frame(iso_o = node_names24, pageRank_unique = pageRank23, close_unique = closeness23, outdegree_unique = outdegree23, indegree_unique = indegree23,local_clust_tt_unique = lct231, local_clust_out_unique = lct232)
centrality_df23
write.csv(centrality_df23, "../data/cleaned/network_metrics_unique2023.csv")
```


```{r}
metric_time_u <- data.frame(TIME_PERIOD = c(2000, 2001, 2002, 2003, 2004, 2005, 2006, 2007, 2008,
                                          2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017,
                                          2018, 2019, 2020, 2021, 2022, 2023),
                   Global_CC_Cl_unique = c(clustcoef(g1, method ="Clemente")$total$globalcc,
                                         clustcoef(g2, method = "Clemente")$total$globalcc,
                                         clustcoef(g3, method = "Clemente")$total$globalcc,
                                         clustcoef(g4, method = "Clemente")$total$globalcc,
                                         clustcoef(g5, method = "Clemente")$total$globalcc,
                                         clustcoef(g6, method = "Clemente")$total$globalcc,
                                         clustcoef(g7, method ="Clemente")$total$globalcc,
                                         clustcoef(g8, method = "Clemente")$total$globalcc,
                                         clustcoef(g9, method = "Clemente")$total$globalcc,
                                         clustcoef(g10, method = "Clemente")$total$globalcc,
                                         clustcoef(g11, method = "Clemente")$total$globalcc,
                                         clustcoef(g12, method = "Clemente")$total$globalcc,
                                         clustcoef(g13, method ="Clemente")$total$globalcc,
                                         clustcoef(g14, method = "Clemente")$total$globalcc,
                                         clustcoef(g15, method = "Clemente")$total$globalcc,
                                         clustcoef(g16, method = "Clemente")$total$globalcc,
                                         clustcoef(g17, method = "Clemente")$total$globalcc,
                                         clustcoef(g18, method = "Clemente")$total$globalcc,
                                         clustcoef(g19, method ="Clemente")$total$globalcc,
                                         clustcoef(g20, method = "Clemente")$total$globalcc,
                                         clustcoef(g21, method = "Clemente")$total$globalcc,
                                         clustcoef(g22, method = "Clemente")$total$globalcc,
                                         clustcoef(g23, method = "Clemente")$total$globalcc,
                                         clustcoef(g24, method = "Clemente")$total$globalcc),
                   Global_CC_Fg_unique = c(clustcoef(g1, method = "Clemente")$out$globalcc,
                                         clustcoef(g2, method = "Clemente")$out$globalcc,
                                         clustcoef(g3, method = "Clemente")$out$globalcc,
                                         clustcoef(g4, method = "Clemente")$out$globalcc,
                                         clustcoef(g5, method = "Clemente")$out$globalcc,
                                         clustcoef(g6, method = "Clemente")$out$globalcc,
                                         clustcoef(g7, method = "Clemente")$out$globalcc,
                                         clustcoef(g8, method = "Clemente")$out$globalcc,
                                         clustcoef(g9, method = "Clemente")$out$globalcc,
                                         clustcoef(g10, method = "Clemente")$out$globalcc,
                                         clustcoef(g11, method = "Clemente")$out$globalcc,
                                         clustcoef(g12, method = "Clemente")$out$globalcc,
                                         clustcoef(g13, method = "Clemente")$out$globalcc,
                                         clustcoef(g14, method = "Clemente")$out$globalcc,
                                         clustcoef(g15, method = "Clemente")$out$globalcc,
                                         clustcoef(g16, method = "Clemente")$out$globalcc,
                                         clustcoef(g17, method = "Clemente")$out$globalcc,
                                         clustcoef(g18, method = "Clemente")$out$globalcc,
                                         clustcoef(g19, method = "Clemente")$out$globalcc,
                                         clustcoef(g20, method = "Clemente")$out$globalcc,
                                         clustcoef(g21, method = "Clemente")$out$globalcc,
                                         clustcoef(g22, method = "Clemente")$out$globalcc,
                                         clustcoef(g23, method = "Clemente")$out$globalcc,
                                         clustcoef(g24, method = "Clemente")$out$globalcc),
                  Avg_CC_Cl_unique = c(mean(clustcoef(g1, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g2, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g3, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g4, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g5, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g6, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g7, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g8, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g9, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g10, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g11, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g12, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g13, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g14, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g15, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g16, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g17, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g18, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g19, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g20, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g21, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g22, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g23, method = "Clemente")$total$localcc),
                                      mean(clustcoef(g24, method = "Clemente")$total$localcc)),
                  Avg_CC_Fg_unique = c(mean(clustcoef(g1, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g2, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g3, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g4, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g5, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g6, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g7, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g8, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g9, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g10, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g11, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g12, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g13, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g14, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g15, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g16, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g17, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g18, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g19, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g20, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g21, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g21, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g23, method = "Clemente")$out$localcc),
                                      mean(clustcoef(g24, method = "Clemente")$out$localcc)),
                  assortcoef_unique = c(assortcoef(g1), 
                                      assortcoef(g2), 
                                      assortcoef(g3), 
                                      assortcoef(g4),
                                      assortcoef(g5), 
                                      assortcoef(g6), 
                                      assortcoef(g7), 
                                      assortcoef(g8),
                                      assortcoef(g9), 
                                      assortcoef(g10), 
                                      assortcoef(g11), 
                                      assortcoef(g12),
                                      assortcoef(g13), 
                                      assortcoef(g14), 
                                      assortcoef(g15), 
                                      assortcoef(g16),
                                      assortcoef(g17), 
                                      assortcoef(g18), 
                                      assortcoef(g19), 
                                      assortcoef(g20),
                                      assortcoef(g21), 
                                      assortcoef(g22), 
                                      assortcoef(g23), 
                                      assortcoef(g24)))

```

```{r}
metric_time_u
```


```{r}
write.csv(metric_time_u, "../data/cleaned/network_metrics_timeseries_unique.csv")
```



```{r}
vcount(un00)
vcount(un01)
vcount(un02)
vcount(un03)
vcount(un04)
vcount(un05)
vcount(un06)
vcount(un07)
vcount(un08)
vcount(un09)
vcount(un10)
vcount(un11)
vcount(un12)
vcount(un13)
vcount(un14)
vcount(un15)
vcount(un16)
vcount(un17)
vcount(un18)
vcount(un19)
vcount(un20)
vcount(un21)
vcount(un22)
vcount(un23)
```



